\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{enumitem}

\geometry{margin=1in}

% --- Listings (Python/JSON) ---
\lstdefinestyle{auditcode}{
  basicstyle=\ttfamily\footnotesize,
  columns=fullflexible,
  breaklines=true,
  keepspaces=true,
  showstringspaces=false,
  upquote=true
}
\lstset{style=auditcode}

% --- Theorem environments ---
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

% --- Notation helpers ---
\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\RePart}{\operatorname{Re}}
\newcommand{\ImPart}{\operatorname{Im}}
\newcommand{\abs}[1]{\left|#1\right|}
\newcommand{\dist}{\operatorname{dist}}

\title{A Width--2 Boundary Program for Excluding Off--Axis Quartets\\
with a Certified Tail Criterion and a Finite--Height Front--End (v43)}
\author{Dylan Anthony Dupont}
\date{v41 compiled: 2026-01-28}

\begin{document}
\maketitle

\begin{abstract}
This is \textbf{v43} of the RH Convergence Program. This build \emph{locks the geometry/endpoint redesign} (GEO--C4): a hinge--centered trig contour in the $v$--plane together with a single \emph{orthogonal harmonic extraction} endpoint built from the two--sided shift--difference log--derivative $\mathcal D_{a,h}$.

\smallskip
The \emph{active closure chain} is now:
\[
\text{off--axis quartet }(\pm a\pm i m)
\Longrightarrow 
\text{forced $k=2$ harmonic on }C_{m,\delta}
\Longrightarrow 
\Phi^\star(m,a,\delta,h)\ge c_0
\]
while the only remaining mathematical frontier is an RH--free upper estimate $\Phi^\star=o(1)$ at the nominal scale $\delta=\eta a/(\log(m+3))^2$ (with monotone admissibility shrink), obtained from unconditional bounds for $E'/E$ and its $(v,t)$--derivatives on \emph{shifted hinge circles}.

\smallskip
All earlier S5$'$ ``defect endpoint'' candidates and aligned--box micro--coupling routes are retained as \emph{archived NO--GO examples}; they are no longer load--bearing in the active chain.
\end{abstract}


\tableofcontents

\section*{Executive Proof Status}
\addcontentsline{toc}{section}{Executive Proof Status}

\paragraph{What this manuscript is / is not.}
\begin{itemize}[leftmargin=*,itemsep=2pt]
  \item It is a formalization of a \emph{boundary-only} strategy to rule out off-axis zeros for the completed zeta object.
  \item It is \emph{not} a finished proof claim: the single remaining analytic obligation is stated explicitly as \textbf{UE-INPUT} (Box~\ref{box:ue-input-v43}).
  \item Every lemma not marked \textsf{OPEN} is intended to be proof-grade and local, with explicit dependencies and monotone shrink conventions.
\end{itemize}

\paragraph{Proof status.}
\noindent\textbf{Status (v43):} \emph{geometry locked; single active analytic frontier}. We adopt the GEO--C4 witness family (hinge-centered circles) and a single harmonic endpoint. All prior S5$'$ ``defect endpoint'' candidates are retained only as \emph{archived NO--GO diagnostics}.

\medskip
\noindent\textbf{Truth-latched NO--GO constraints (scope-audited).}
\begin{enumerate}[leftmargin=*,itemsep=2pt]
  \item \textbf{(S5$'$ cancellation)} The centered defect endpoint for $\mathcal L_a$ cannot inherit $\pi/2$ forcing from one quartet: it is $O(\delta/a)$ (Section~\ref{sec:S5-frontier}).
  \item \textbf{($\delta$-inert resonance)} Pointwise/sidewise endpoints built from shift-quotients can be $\delta$-inert under near-resonant second quartets unless the geometry is redesigned.
  \item \textbf{(Side-length ceiling)} Any endpoint built as a side integral has magnitude $\lesssim \delta \sup|f|$; shrink alone cannot create forcing.
  \item \textbf{(NG-$\Delta a$-A)} Aligned boxes at $(a+i m)$ with micro-coupling $h\sim\delta$ suppress the two-sided field by $\delta h/a^2$.
  \item \textbf{(Pointwise UE ceiling)} A purely pointwise/supremum upper estimate on $E'/E$ along a boundary is too weak to contradict forcing at the nominal scale.
  \item \textbf{(Projection endpoints: audited scope)} ``Projection endpoints are dead'' applies only to projections that annihilate the \emph{forced local kernel} or that reduce to pointwise/supremum UE. GEO--C4 uses the $k=2$ harmonic of the \emph{dipole kernel} generated by $\mathcal D_{a,h}$ on hinge circles; this does not fall under the NO--GO.
\end{enumerate}

\medskip
\noindent\textbf{Single active blocker (v43):} \textbf{UE-INPUT} for the GEO--C4 endpoint $\Phi^\star$ (Box~\ref{box:ue-input-v43}). All other items are bookkeeping/citation polishing.

\paragraph{Reproducibility posture (v43).}
We ship a minimal certificate harness for the tail inequality checks and envelope numerics. These certificates are \emph{supporting} (not a proof of RH). See Appendix~\ref{app:repro} and the directory \texttt{v43\_repro\_pack/}.

\part{Reader's Guide / Definitions and Reduction}
\label{part:guide}

\section{Width--2 normalization}
\label{sec:width2}

Let $s$ denote the usual complex variable for $\zeta(s)$. We pass to the width--$2$ coordinate
\[
u:=2s,\qquad \zeta_2(u):=\zeta(u/2).
\]
Define the width--$2$ completed zeta
\[
\Lambda_2(u):=\pi^{-u/4}\Gamma(u/4)\zeta(u/2).
\]
Then $\Lambda_2$ is \emph{meromorphic} (simple poles at $u=0$ and $u=2$) and satisfies the functional equation
\[
\Lambda_2(u)=\Lambda_2(2-u).
\]
Define the entire completion
\[
\Xi_2(u):=\xi(u/2)=\frac{u(u-2)}{8}\,\Lambda_2(u),
\]
so that $\Xi_2$ is entire and obeys $\Xi_2(u)=\Xi_2(2-u)$.

We recenter at $u=1$:
\[
v:=u-1,\qquad E(v):=\Xi_2(1+v).
\]
Then $E$ is entire and satisfies the evenness relation
\[
E(v)=E(-v),
\]
and complex conjugation gives $E(\overline v)=\overline{E(v)}$.

\begin{remark}[Zeros]
The zeros of $\Xi_2(u)=\xi(u/2)$ are exactly the \emph{nontrivial} zeros of $\zeta(s)$ under the map $u=2s$, with multiplicity.
All boxes used in the tail program lie at heights $m\ge 10$, so the only zeros that can occur in the relevant local windows are nontrivial zeros.
\end{remark}

\section{Heights and horizontal displacement (RH--free)}
\label{sec:heights}

Let $\rho=\beta+i\gamma$ be any nontrivial zero of $\zeta(s)$ (no assumption on $\beta$). In width--2
we write
\begin{equation}
  u_\rho := 2\rho = (1+a)+im,\qquad a:=2\beta-1\in(-1,1),\qquad m:=2\gamma>0.
\end{equation}
Thus RH is equivalent to $a=0$ for every nontrivial zero.

\section{Quartet symmetry in width--2}
\label{sec:quartets}

The functional equation and conjugation imply that any off--axis zero with parameters $(a,m)$
produces a quartet
\begin{equation}
  \{\,1\pm a\pm im\,\} \subset \{u\in\C: \Xi_2(u)=0\}.
\end{equation}
In the centered $v$--coordinate this becomes $\{\pm a\pm im\}\subset\{v\in\C:E(v)=0\}$.

\section{Finite-height front-end after lowering the tail anchor}
\label{sec:frontend}

Once the tail anchor is lowered to $m_\star$, the analytic tail argument covers all $m\ge m_\star$.
The remaining region corresponds to classical heights
\begin{equation}
  0 < \ImPart(s) < H_0 := m_\star/2.
\end{equation}
In v31 we take $m_\star=10$, hence $H_0=5$.

\begin{definition}[Front-end statement]
\label{def:frontend}
We say that \emph{RH holds up to height $H_0$} if every nontrivial zero $\rho=\beta+i\gamma$ with
$0<\gamma\le H_0$ satisfies $\beta=1/2$.
\end{definition}

\begin{remark}[How v31 discharges the front-end]
The required statement for v31 is RH up to height $H_0=5$.
This is a tiny special case of published rigorous verifications of RH to enormous heights.
For example, Platt--Trudgian prove RH for all zeros with $0<\gamma\le 3\cdot 10^{12}$ using interval
arithmetic, which immediately implies RH up to $H_0=5$.
Appendix~\ref{app:frontend} records this discharge in a pinned JSON file.
\end{remark}

\part{Self-Contained Boundary Program and Tail Closure}
\label{part:core}

\section{Aligned boxes and the $\delta(m)$ scale}
\label{sec:boxes}

Let $m>0$ and $\alpha\in(0,1]$. Fix a parameter $\eta\in(0,1)$ and define the \emph{nominal} box scale
\begin{equation}
  \delta_0=\delta_0(m,\alpha):=\frac{\eta\alpha}{(\log m)^2}.
\end{equation}
We will work with aligned boxes $B(\alpha,m,\delta)$ at scales $0<\delta\le \delta_0$.
By default one may take $\delta=\delta_0$, but later (Definition~\ref{def:collar-admissible}) we allow
shrinking $\delta$ to enforce $\kappa$--admissibility; this is non-circular and monotone-safe
(Lemmas~\ref{lem:collar-existence} and \ref{lem:delta-shrink-monotone}).

Define the (width--2) box centered at $\alpha+im$ by
\begin{equation}
  B(\alpha,m,\delta) := \{\,v\in\C: \abs{\RePart v-\alpha}\le \delta,\ \abs{\ImPart v-m}\le \delta\,\}.
\end{equation}
We will also use the symmetric dial centers $v_\pm:=\pm\alpha+im$.

\section{Local factor and finiteness}
\label{sec:local-factor}

For a fixed $m>0$, let
\begin{equation}\label{eq:Z-window}
  Z(m):=\{\,\rho: E(\rho)=0,\ \abs{\ImPart \rho-m}\le 1\,\}
\end{equation}
(zeros counted with multiplicity). Define the local zero factor and residual:
\begin{equation}\label{eq:zloc-def}
  Z_{\mathrm{loc}}(v):=\prod_{\rho\in Z(m)} (v-\rho)^{m_\rho}.
\end{equation}
\begin{equation}\label{eq:F-def}
  F(v):=\frac{E(v)}{Z_{\mathrm{loc}}(v)}.
\end{equation}

\begin{lemma}[Finiteness of $Z_{\mathrm{loc}}$]
\label{lem:zloc-finite}
For each fixed $m>0$ the set $Z(m)$ is finite; hence $Z_{\mathrm{loc}}$ is a finite product and $F$ is
meromorphic globally and analytic in any neighborhood of $\partial B(\alpha,m,\delta)$ that contains
no zeros of $E$.
\end{lemma}

\begin{proof}
Nontrivial zeros of $\zeta$ satisfy $0<\beta<1$, hence in the $v$--coordinate one has
$\RePart v\in(-1,1)$ for all nontrivial zeros.
Therefore the set
\(\{\abs{\ImPart v-m}\le 1\}\cap\{\abs{\RePart v}\le 1\}\)
is compact.
Since $E$ is entire and its zeros are discrete, only finitely many zeros can lie in this compact set.
\end{proof}

\section{Residual envelope bound and the constants ledger}
\label{sec:ledger}
\begin{remark}[Constant gate for the residual term (what is and is not assumed)]
\label{rem:residual-constant-gate}
The tail criterion uses a bound of the form
\[
\sup_{v\in\partial B(\alpha,m,\delta)}\Bigl|\frac{F'(v)}{F(v)}\Bigr|
\ \le\ C_1\log m + C_2,
\]
with constants that must be (i) unconditional (not RH-equivalent) and (ii) uniform in
$(\alpha,\delta,\eta,\kappa)$ once $m\ge 10$ and $0<\alpha\le 1$.
The proof below reduces this to standard RH-free bounds for $\zeta'/\zeta$ in the critical strip with
local-zero subtraction, plus a Stirling-type bound for $\Gamma'/\Gamma$.
\end{remark}

\begin{lemma}[Residual envelope inequality (\texorpdfstring{$\delta$}{delta}-uniform)]
\label{lem:residual-envelope}
Fix $m\ge 10$ and $\alpha\in(0,1]$.
Let $\eta\in(0,1]$ and set the nominal width $\delta_0:=\eta\alpha/(\log m)^2$.
Let $\delta\in(0,\delta_0]$ and set $B:=B(\alpha,m,\delta)$.

Define $E$, $Z_{\rm loc}$ and $F:=E/Z_{\rm loc}$ as in \S\ref{sec:local-factor}
(equations \eqref{eq:zloc-def}--\eqref{eq:F-def}).
Assume \emph{boundary-contact} on $\partial B$ (i.e.\ $E\neq 0$ on $\partial B$; hence $F$ is holomorphic on a
neighborhood of $\partial B$).
Then there exist absolute constants $C_1,C_2>0$ (independent of $m,\alpha,\delta,\eta,\kappa$ and of the zero configuration) such that
\[
\sup_{v\in\partial B}\Bigl|\frac{F'(v)}{F(v)}\Bigr|
\ \le\ C_1\log m + C_2.
\]
\end{lemma}

\begin{proof}[Proof sketch with explicit dependency control]
Write $u:=1+v$ and $s:=u/2=(1+v)/2=\sigma+it$.
For $v\in\partial B(\alpha,m,\delta)$ we have $\RePart(s)\in[0,1]$ and
\[
\ImPart(s)=\frac{\ImPart(v)}{2}\in\Bigl[\frac m2-\frac\delta2,\frac m2+\frac\delta2\Bigr].
\]
Since $m\ge 10$ and $\delta\le \delta_0\le 1/(\log 10)^2<1/5$, we have $\ImPart(s)\asymp m$ uniformly in $\delta$.

\smallskip
\noindent\textbf{1) Log-derivative identity in the $s$-frame.}
From $\Xi_2(u)=\frac{u(u-2)}{8}\Lambda_2(u)$ and $\Lambda_2(u)=\pi^{-u/4}\Gamma(u/4)\zeta(u/2)$ we obtain,
for $u=1+v$,
\[
\frac{E'(v)}{E(v)}
=\frac{\Xi_2'(u)}{\Xi_2(u)}
=\Bigl(\frac{1}{u}+\frac{1}{u-2}\Bigr)\ -\ \frac14\log\pi\ +\ \frac14\frac{\Gamma'}{\Gamma}\Bigl(\frac{u}{4}\Bigr)
\ +\ \frac12\,\frac{\zeta'}{\zeta}(s),
\qquad (u=1+v,\ s=u/2).
\]
Since $u=1+v$ has $\ImPart(u)=m\ge 10$, the completion terms $(1/u+1/(u-2))$ are $O(1/m)$ on $\partial B$ and are absorbed into the absolute constants in the bound.

Moreover, since $v=2s-1$, the local factor derivative satisfies
\[
\frac{Z_{\rm loc}'(v)}{Z_{\rm loc}(v)}=\sum_{\rho\in Z(m)}\frac{m_\rho}{v-\rho}
=\frac12\sum_{\rho_s\in Z_s(m)}\frac{m_{\rho_s}}{s-\rho_s},
\]
where $Z_s(m)$ denotes the corresponding multiset of nontrivial zeros $\rho_s=\beta+i\gamma$ of $\zeta(s)$
with $|\gamma-\tfrac m2|\le \tfrac12$.

Therefore
\[
\frac{F'(v)}{F(v)}
=\frac{E'(v)}{E(v)}-\frac{Z_{\rm loc}'(v)}{Z_{\rm loc}(v)}
= -\frac14\log\pi + \frac14\frac{\Gamma'}{\Gamma}\Bigl(\frac{1+v}{4}\Bigr)
+\frac12\Biggl(\frac{\zeta'}{\zeta}(s) - \sum_{\rho_s\in Z_s(m)}\frac{m_{\rho_s}}{s-\rho_s}\Biggr).
\]

\smallskip
\noindent\textbf{2) RH-free residual bound for $\zeta'/\zeta$ with local-zero subtraction.}
A standard ``local-zero decomposition'' (unconditional) asserts that there exist absolute constants
$A_\zeta,B_\zeta$ such that for $0\le\sigma\le 1$ and $t\ge 5$,
\[
\Bigl|\frac{\zeta'}{\zeta}(\sigma+it) - \sum_{|\gamma-t|\le 1}\frac{1}{(\sigma+it)-\rho}\Bigr|
\ \le\ A_\zeta\log(t+2) + B_\zeta.
\tag{$\star$}
\]
(For a self-contained route, ($\star$) can be derived from the Hadamard product for $\xi(s)$ plus a
Riemann--von Mangoldt bound for $N(T)$; otherwise cite a standard reference.)

For $v\in\partial B$ we have $|t-\tfrac m2|\le \delta/2<1/10$, hence every zero in $Z_s(m)$
satisfies $|\gamma-t|\le 1$ and is included in the sum in ($\star$).
Thus
\[
\frac{\zeta'}{\zeta}(s)-\sum_{\rho_s\in Z_s(m)}\frac{1}{s-\rho_s}
=
\Bigl(\frac{\zeta'}{\zeta}(s)-\sum_{|\gamma-t|\le 1}\frac{1}{s-\rho}\Bigr)
+\sum_{\substack{|\gamma-t|\le 1\\|\gamma-\tfrac m2|>1/2}}\frac{1}{s-\rho}.
\]
In the remaining sum we have $|\gamma-t|\ge 1/2-|t-\tfrac m2|\ge 2/5$, hence $|s-\rho|\ge 2/5$ and each term has modulus $\le 5/2$.
The number of zeros with $|\gamma-t|\le 1$ is bounded by the manuscript's explicit local window majorant
(Lemma~\ref{lem:Nloc-logm}) at height $\asymp m$, so this difference-of-windows sum is $\ll \log m$.

Combining these bounds yields absolute constants $A_{\rm res},B_{\rm res}$ such that
\[
\Bigl|\frac{\zeta'}{\zeta}(s)-\sum_{\rho_s\in Z_s(m)}\frac{1}{s-\rho_s}\Bigr|
\ \le\ A_{\rm res}\log m + B_{\rm res},
\]
uniformly for all $v\in\partial B$ and all $\delta\in(0,\delta_0]$.

\smallskip
\noindent\textbf{3) Gamma factor bound (Stirling, uniform in $\delta$).}
For $z=(1+v)/4$ we have $\RePart(z)\in[1/4,3/4]$ and $|\ImPart(z)|\asymp m$.
A uniform Stirling-type bound gives
\[
\Bigl|\frac{\Gamma'}{\Gamma}(z)\Bigr| \le \log(|\ImPart(z)|+2) + C_\Gamma
\ \le\ \log(m+2)+C_\Gamma,
\]
with an absolute constant $C_\Gamma$.

\smallskip
\noindent\textbf{4) Conclusion.}
Insert the bounds from (2)--(3) into the identity in (1), and absorb harmless constants into $(C_1,C_2)$.
All constants are independent of $(\alpha,\delta,\eta,\kappa)$ because:
(i) $\sigma$ ranges over a fixed compact interval $[0,1]$,
(ii) $t\asymp m$ with $m\ge 10$ uniformly for $\delta\le\delta_0$, and
(iii) the difference-of-windows sum is controlled by Lemma~\ref{lem:Nloc-logm}, which is unconditional.
\end{proof}

\begin{remark}[Hard gate / certificates (v40)]
The tail harness in Appendix~\ref{app:certificate} uses explicit numerical interval enclosures for the
constant ledger (e.g.\ $C_1,C_2,C_{\rm up},C_h'',\kappa$) stored in
\texttt{v36\_repro\_pack/v36\_constants\_m10.json}.
It evaluates the tail inequality for a pinned parameter choice and records the UE exponent $p$ explicitly.
This is an \emph{audit harness} only: it does not certify that the constants file is correct, and it does not,
by itself, yield a uniform tail closure.
An unconditional proof therefore still requires a referee-acceptable certification of the analytic constant ledger,
and a resolution of the UE--Gate (Remark~\ref{rem:UE-gate}).
\end{remark}

\section{Short-side forcing}
\label{sec:forcing}

Assume an off-axis pair at height $m$ with displacement $a>0$ exists. On an aligned box with
$\alpha=a$, the two upper zeros in the centered $v$--plane are at $v=\pm a+im$. The pair factor
\begin{equation}
  Z_{\mathrm{pair}}(v):=(v-(a+im))(v-(-a+im))
\end{equation}
produces a large phase rotation on the near vertical side.

\begin{lemma}[Short-side forcing lower bound]
\label{lem:short-side-forcing}
Let $I_+:=\{\alpha+iy: \abs{y-m}\le\delta\}$ with $\abs{\alpha-a}\le\delta$. Then
\begin{equation}
  \Delta_{I_+}\arg Z_{\mathrm{pair}}
  = 2\arctan\!\left(\frac{\delta}{\abs{\alpha-a}}\right)
    +2\arctan\!\left(\frac{\delta}{\alpha+a}\right)
  \ge \frac{\pi}{2}.
\end{equation}
\end{lemma}


\begin{lemma}[Single-box forcing is constant-limited]
\label{lem:force-constant-limited}
In the forcing setup of Lemma~\ref{lem:short-side-forcing}, the total phase variation of the pair factor along $I_+$ satisfies
\[
\Delta_{I_+}\arg Z_{\mathrm{pair}}\le 2\pi,
\]
uniformly in the height $m$.
Consequently the forcing constant $c$ appearing in the tail inequality (Theorem~\ref{thm:tail-inequality}) is an absolute constant,
independent of $m$; in particular the forcing side cannot grow like $\log m$ (or any unbounded function of $m$) as $m\to\infty$.
\end{lemma}

\begin{proof}
On $I_+=\{\alpha+iy:\ |y-m|\le\delta\}$ one has
\[
Z_{\mathrm{pair}}(\alpha+iy)=\bigl((\alpha-a)+i(y-m)\bigr)\bigl((\alpha+a)+i(y-m)\bigr).
\]
Along $y\in[m-\delta,m+\delta]$ the argument of each linear factor varies by at most $\pi$ (it is an $\arctan$ function whose range lies in an interval of length $\le\pi$),
so the argument of the product varies by at most $2\pi$, uniformly in $m$.
The forcing chain converts a fixed positive portion of $\Delta_{I_+}\arg Z_{\rm pair}$ into the constant $c$ with fixed conversion scalars,
so $c$ is necessarily $O(1)$.
\end{proof}

\section{Outer factorization and the inner quotient (Bridge 1)}
\label{sec:bridge1}

We work on a fixed box $B=B(\alpha,m,\delta)$ and write $B^\circ$ for its interior.
Assume boundary-contact: $E\neq 0$ on $\partial B$ (this will be enforced later by $\kappa$--admissibility; see Definition~\ref{def:collar-admissible} and Lemma~\ref{lem:collar-existence}).

\begin{lemma}[Dirichlet outer factor on a box]
\label{lem:outer_dirichlet_box}
Let $B=B(\alpha,m,\delta)$ be the closed rectangle and $B^\circ$ its interior.
Assume $E$ is holomorphic on a neighborhood of $\overline{B}$ and $E\neq 0$ on $\partial B$.
Then $\log|E|\in C(\partial B)$.
Let $U\in C(\overline{B})\cap \mathrm{Harm}(B^\circ)$ be the unique solution of the Dirichlet problem
with boundary data $U|_{\partial B}=\log|E|$.
Since $B^\circ$ is simply connected, there exists a harmonic conjugate $V$ on $B^\circ$
(unique up to an additive constant) such that $U+iV$ is holomorphic on $B^\circ$.
Define
\[
G_{\mathrm{out}}(v):=\exp(U(v)+iV(v)),\qquad v\in B^\circ.
\]
Then $G_{\mathrm{out}}$ is holomorphic and zero-free on $B^\circ$, satisfies $|G_{\mathrm{out}}(v)|=e^{U(v)}$ for $v\in B^\circ$, and
\[
\lim_{z\to\xi,\ z\in B^\circ}|G_{\mathrm{out}}(z)| = |E(\xi)|\qquad(\xi\in\partial B).
\]
\end{lemma}

\begin{proof}
Continuity of $\log|E|$ on $\partial B$ follows from $E\neq 0$ on $\partial B$.
Existence and uniqueness of $U$ on a rectangle are standard.
Since $B^\circ$ is simply connected, $U$ admits a harmonic conjugate $V$ on $B^\circ$, unique up to an additive constant.
The function $U+iV$ is holomorphic, hence so is $G_{\mathrm{out}}=\exp(U+iV)$, and it is zero-free.
Finally $|G_{\mathrm{out}}|=e^U$ on $B^\circ$, and by continuity of $U$ on $\overline{B}$ we have
$e^{U(\xi)}=|E(\xi)|$ on $\partial B$, yielding the boundary modulus identity in interior-limit form.
\end{proof}

Define on $B^\circ$ the inner quotient
\[
W(v):=\frac{E(v)}{G_{\mathrm{out}}(v)}.
\]
Then $W$ is holomorphic on $B^\circ$ and $|W|=1$ on $\partial B$ in the sense of interior limits in modulus.

\begin{proposition}[Bridge 1: zero-free inner collapse]
\label{prop:bridge1}
Assume the setup of Lemma~\ref{lem:outer_dirichlet_box} and define $W=E/G_{\mathrm{out}}$ on $B^\circ$.
If $W$ is zero-free on $B^\circ$ (equivalently, $E$ is zero-free on $B^\circ$), then $W$ is constant on $B^\circ$; in fact
$W\equiv e^{i\theta_B}$ for some $\theta_B\in\R$.
\end{proposition}

\begin{proof}
Since $W$ is zero-free on $B^\circ$ and $G_{\mathrm{out}}$ is zero-free, the function $E$ is zero-free on $B^\circ$.
Because $B^\circ$ is simply connected, $E$ admits a holomorphic logarithm on $B^\circ$, so $\log|E|$ is harmonic on $B^\circ$.
By construction $U$ is harmonic on $B^\circ$, continuous on $\overline{B}$, and equals $\log|E|$ on $\partial B$.
Thus $U-\log|E|$ is harmonic on $B^\circ$ with zero boundary values, so by Dirichlet uniqueness $U\equiv \log|E|$ on $B^\circ$.
Therefore for $v\in B^\circ$,
\[
|W(v)|=\frac{|E(v)|}{|G_{\mathrm{out}}(v)|}=\frac{|E(v)|}{e^{U(v)}}=\frac{|E(v)|}{e^{\log|E(v)|}}=1.
\]
An analytic function of constant modulus on a connected open set is constant, hence $W\equiv e^{i\theta_B}$.
\end{proof}

\begin{remark}[Boundary modulus convention]
\label{rem:boundary_modulus}
Under boundary-contact, $U$ extends continuously to $\partial B$ and satisfies $U|_{\partial B}=\log|E|$.
Hence $|G_{\mathrm{out}}|=|E|$ holds pointwise on $\partial B$ as interior limits in modulus, and therefore
$|W|=1$ holds pointwise in modulus on $\partial B$.
In boundary integral estimates this may be used in the a.e.\ sense without change.
\end{remark}


\begin{remark}[No converse: boundary modulus does not exclude interior zeros]
\label{rem:no-converse}
Lemma~\ref{lem:outer_dirichlet_box} implies that under boundary-contact the quotient $W:=E/G_{\mathrm{out}}$ satisfies
$|W|=1$ on $\partial B$ (in the interior boundary-limit sense of Remark~\ref{rem:boundary_modulus}).
This condition alone does \emph{not} imply that $W$ is zero-free or constant on $B^\circ$:
nonconstant holomorphic functions on $B^\circ$ can have $|W|=1$ on $\partial B$ and still possess prescribed interior zeros
(e.g.\ via conformal transport of finite Blaschke products from the unit disc).
Thus Proposition~\ref{prop:bridge1} is strictly one-directional: the additional hypothesis ``$W$ is zero-free on $B^\circ$'' is essential.
\end{remark}

\section{Shape-only invariance and the envelope constants}
\label{sec:shape-only}

Let $T(v):=(v-(\alpha+im))/\delta$, mapping $\partial B$ affinely onto the fixed square boundary
$\partial Q$ with $Q=[-1,1]^2$.

\begin{lemma}[Shape-only invariance]
\label{lem:shape-only}
Any constant arising solely from geometric or boundary-operator estimates on $\partial B$ that are
invariant under affine rescaling depends only on $\partial Q$ and is independent of $(\alpha,m,\delta)$.
\end{lemma}

\begin{proof}
Under $T$, arclength scales by $\delta$ and tangential derivatives by $1/\delta$. After normalization,
all purely geometric quantities and operator norms reduce to fixed quantities on $\partial Q$.
\end{proof}

\begin{lemma}[Boundary-to-center evaluation in $L^2$ (sharp $\delta^{-1/2}$)]
\label{lem:eval-L2}
Let $B=B(\alpha,m,\delta)$ be a box and let $v_0$ be its center.
Let $u$ be harmonic on $B^\circ$ and assume its boundary trace lies in $L^2(\partial B,ds)$.
Then, writing $P_B(v_0,\xi)=d\omega^B_{v_0}/ds(\xi)$ for the Poisson kernel of $B$ at $v_0$,
\[
\abs{u(v_0)}\le \|P_B(v_0,\cdot)\|_{L^2(\partial B,ds)}\;\|u\|_{L^2(\partial B,ds)}.
\]
Under the similarity $T(\xi)=(\xi-v_0)/\delta$ mapping $\partial B$ onto $\partial Q$,
\[
\|P_B(v_0,\cdot)\|_{L^2(\partial B,ds)}=\delta^{-1/2}\,\|P_Q(0,\cdot)\|_{L^2(\partial Q,ds)}.
\]
In particular the exponent $\delta^{-1/2}$ is sharp (witnessed by the constant harmonic function $u\equiv 1$).
\end{lemma}

\begin{proof}
For harmonic $u$ on $B^\circ$ with $L^2$ trace on $\partial B$, the Poisson representation gives
\[
u(v_0)=\int_{\partial B}u(\xi)\,d\omega^B_{v_0}(\xi)
=\int_{\partial B}u(\xi)\,P_B(v_0,\xi)\,ds(\xi).
\]
Cauchy--Schwarz yields $\abs{u(v_0)}\le \|P_B(v_0,\cdot)\|_{L^2}\|u\|_{L^2}$.

For the scaling: under $T$, arclength scales by $ds=\delta\,ds_Q$ and Poisson kernels scale by
$P_B(v_0,\xi)=\delta^{-1}P_Q(0,T(\xi))$. Hence
\[
\int_{\partial B}P_B(v_0,\xi)^2\,ds(\xi)
=\int_{\partial Q}\delta^{-2}P_Q(0,\zeta)^2\,\delta\,ds_Q(\zeta)
=\delta^{-1}\int_{\partial Q}P_Q(0,\zeta)^2\,ds_Q(\zeta),
\]
giving $\|P_B(v_0,\cdot)\|_{L^2}=\delta^{-1/2}\|P_Q(0,\cdot)\|_{L^2}$.

Sharpness: for $u\equiv 1$ we have $\abs{u(v_0)}=1$ and $\|u\|_{L^2(\partial B)}=\sqrt{|\partial B|}\asymp \delta^{1/2}$,
so the inequality forces $\|P_B(v_0,\cdot)\|_{L^2}\gtrsim \delta^{-1/2}$.
\end{proof}

\begin{lemma}[Upper envelope bound (outer-aligned form)]
\label{lem:upper-envelope}
Let $B=B(\pm a,m,\delta)$ be an aligned box and let $G_{\rm out}$ be the outer factor on $B$
constructed from $\log|E|$ on $\partial B$ (Section~\ref{sec:bridge1}). Define the inner quotient
\[
W(v):=\frac{E(v)}{G_{\rm out}(v)}.
\]
Assume the boundary-contact convention: $E$ has no zeros on $\partial B$ (hence $W$ has unimodular
boundary values a.e.). For each sign $\pm$ let $v_\pm:=\pm a+im$ and let $e^{i\varphi_0^\pm}\in\mathbb T$
be an $L^2(\partial B,ds)$-best constant phase,
\[
e^{i\varphi_0^\pm}\in\arg\min_{|c|=1}\int_{\partial B}|W(v)-c|^2\,ds(v).
\]
Then there exists a \emph{shape-only} constant $C_{\rm up}>0$ (depending only on the normalized square
$Q=[-1,1]^2$) such that
\begin{equation}
\label{eq:UE-EoverE}
\sum_{\pm}\bigl|W(v_\pm)-e^{i\varphi_0^\pm}\bigr|
\ \le\ 2\,C_{\rm up}\,\delta\,\sup_{v\in\partial B}\Bigl|\frac{E'(v)}{E(v)}\Bigr|.
\end{equation}
One admissible explicit definition is
\[
C_{\rm up}
:=\Big(\sup_{\xi\in\partial Q}P_Q(0,\xi)\Big)^{1/2}\cdot \frac{4}{\pi}\cdot \sqrt{8}\cdot\bigl(1+\|H_{\partial Q}\|_{L^2\to L^2}\bigr),
\]
where $P_Q(0,\xi)=d\omega^Q_0/ds(\xi)$ is the Poisson kernel of $Q$ at the center $0$ with respect to
arclength on $\partial Q$, and $H_{\partial Q}$ is the boundary conjugation (Hilbert/Cauchy) operator
on $\partial Q$.
\end{lemma}

\begin{remark}[No residual proxying in the upper envelope]
\label{rem:no-proxying}
Lemma~\ref{lem:upper-envelope} controls the inner quotient $W=E/G_{\rm out}$ and therefore depends on
$\sup_{\partial B}|E'/E|$.
Residual bounds for $F=E/Z_{\rm loc}$ control $\sup_{\partial B}|F'/F|$ and do \emph{not} by themselves
bound $\sup_{\partial B}|E'/E|$.
Whenever the residual envelope is used to control dial deviation, it must be routed through the
log-derivative split $E'/E=F'/F+Z'_{\rm loc}/Z_{\rm loc}$ (Lemma~\ref{lem:logder-split}) together with
the collar bound (Lemma~\ref{lem:Zloc-logder-collar}), yielding Corollary~\ref{cor:UE-residual-local}.
\end{remark}

\begin{proof}
Fix one sign and write $v_0=v_\pm$ and $B=B(\pm a,m,\delta)$.
We record the (RH-free) chain and indicate the scale factors explicitly.
\begin{enumerate}[leftmargin=1.5em]
\item \textbf{Evaluation from the boundary (harmonic measure; produces $\delta^{-1/2}$).}
For any constant $c\in\mathbb T$, subharmonicity of $|W-c|^2$ implies
\[
|W(v_0)-c|^2\le \int_{\partial B}|W(\xi)-c|^2\,d\omega_{v_0}^B(\xi)
=\int_{\partial B}|W(\xi)-c|^2\,P_B(v_0,\xi)\,ds(\xi),
\]
so
\[
|W(v_0)-c|\le \|P_B(v_0,\cdot)\|_{L^\infty(\partial B)}^{1/2}\,\|W-c\|_{L^2(\partial B,ds)}.
\]
Under the similarity $T(\xi)=(\xi-v_0)/\delta$ mapping $\partial B$ onto $\partial Q$,
Poisson kernels scale by
$\|P_B(v_0,\cdot)\|_\infty^{1/2}=\delta^{-1/2}\,\|P_Q(0,\cdot)\|_\infty^{1/2}$.
\item \textbf{Poincar\'e/Wirtinger on $\partial B$ (produces $\delta$).}
For the $L^2$-best constant $c=e^{i\varphi_0^\pm}$ and $|\partial B|=8\delta$,
periodic Poincar\'e on a loop of length $8\delta$ gives
\[
\|W-c\|_{L^2(\partial B)}\le \frac{|\partial B|}{2\pi}\,\|\partial_s W\|_{L^2(\partial B)}
=\frac{4\delta}{\pi}\,\|\partial_s W\|_{L^2(\partial B)}.
\]
\item \textbf{Outer factor control (no $\delta$; uses bounded boundary conjugation).}
Write $\log G_{\rm out}=U+i\widetilde U$ with $U|_{\partial B}=\log|E|$ and $\widetilde U=H_{\partial B}U$.
Differentiating tangentially,
$\partial_s\log G_{\rm out}=\partial_s U+i\,H_{\partial B}(\partial_s U)$.
Since $\log W=\log E-\log G_{\rm out}$,
\[
\|\partial_s\log W\|_{L^2(\partial B)}
\le \bigl(1+\|H_{\partial B}\|_{L^2\to L^2}\bigr)\,\|\partial_s\log E\|_{L^2(\partial B)}
\le \bigl(1+\|H_{\partial B}\|_{L^2\to L^2}\bigr)\,\Big\|\frac{E'}{E}\Big\|_{L^2(\partial B)}.
\]
On $\partial B$ we have $|W|=1$ a.e., hence $|\partial_s W|=|\partial_s\log W|$.
\item \textbf{$L^2$ to $\sup$ (produces $\delta^{1/2}$).}
Using $|\partial B|=8\delta$,
\[
\Big\|\frac{E'}{E}\Big\|_{L^2(\partial B)}\le \sqrt{|\partial B|}\,\sup_{\partial B}\Big|\frac{E'}{E}\Big|
=\sqrt{8\delta}\,\sup_{\partial B}\Big|\frac{E'}{E}\Big|.
\]
\end{enumerate}
Combining the four steps yields
\[
|W(v_0)-e^{i\varphi_0^\pm}|
\le \|P_Q(0,\cdot)\|_\infty^{1/2}\cdot \frac{4}{\pi}\cdot \sqrt{8}\cdot\bigl(1+\|H_{\partial Q}\|_{L^2\to L^2}\bigr)
\cdot \delta\sup_{\partial B}\Big|\frac{E'}{E}\Big|,
\]
where we used the similarity invariance $\|H_{\partial B}\|_{L^2\to L^2}=\|H_{\partial Q}\|_{L^2\to L^2}$.
Summing over $\pm$ gives \eqref{eq:UE-EoverE}.
\end{proof}


\subsection{Local factor split and collar control}
\label{subsec:local-split}

\begin{definition}[Collar-admissible aligned boxes]
\label{def:collar-admissible}
Fix once and for all a collar parameter $\kappa\in(0,1/10)$.
An aligned box $B=B(\alpha,m,\delta)$ is called \emph{$\kappa$--admissible} if
\[
\dist\bigl(\partial B,\,\mathcal Z(E)\bigr)\ge \kappa\delta.
\]
Given any nominal scale $\delta_0>0$ and any center, there exists some $0<\delta\le \delta_0$ for which
$\kappa$--admissibility holds (Lemma~\ref{lem:collar-existence}).
Whenever a chosen box is not $\kappa$--admissible, we shrink $\delta$ until $\kappa$--admissibility holds.
Moreover the assembled tail inequality is monotone-safe under such $\delta$--shrinking
(Lemma~\ref{lem:delta-shrink-monotone}).
\end{definition}

\begin{lemma}[Existence of a $\kappa$--admissible shrink]
\label{lem:collar-existence}
Fix $\kappa\in(0,1/10)$ and a center $v_0\in\C$.
For every $\delta_0>0$ there exists $\delta'\in(0,\delta_0]$ such that the closed box
\[
B(v_0,\delta'):=\{\,v\in\C:\ \|v-v_0\|_\infty\le \delta'\,\}
\]
satisfies
\[
\dist\bigl(\partial B(v_0,\delta'),\,\mathcal Z(E)\bigr)\ge \kappa\delta'.
\]
In particular, given $(\alpha,m)$ and nominal $\delta_0=\eta\alpha/(\log m)^2$, one may always choose a scale
$0<\delta\le\delta_0$ for which $B(\alpha,m,\delta)$ is $\kappa$--admissible.
\end{lemma}

\begin{proof}
Zeros of the entire function $E$ are isolated.
Choose $\varepsilon>0$ such that $\mathcal Z(E)\cap \{\,0<\|v-v_0\|_\infty\le \varepsilon\,\}$ is empty
(if $E(v_0)=0$) or such that $\mathcal Z(E)\cap \{\,\|v-v_0\|_\infty\le \varepsilon\,\}$ is empty
(if $E(v_0)\neq 0$).
Set $\delta':=\min\{\delta_0,\varepsilon/(1+\kappa)\}$.
Then every boundary point satisfies $\|v-v_0\|_\infty=\delta'$.
Any zero $\rho\in\mathcal Z(E)$ is either $\rho=v_0$ (in which case $\dist(v,\rho)=\delta'\ge \kappa\delta'$)
or satisfies $\|\rho-v_0\|_\infty\ge \varepsilon$ (in which case $\dist(v,\rho)\ge \varepsilon-\delta'\ge \kappa\delta'$).
Therefore $\dist(\partial B(v_0,\delta'),\mathcal Z(E))\ge \kappa\delta'$.
\end{proof}



\begin{lemma}[Log-derivative decomposition]
\label{lem:logder-split}
With $Z_{\rm loc}$ and $F$ as in \eqref{eq:zloc-def} and \eqref{eq:F-def}, one has on any region where
$E$ and $Z_{\rm loc}$ are holomorphic and nonvanishing (in particular on $\partial B$ under the boundary-contact convention)
\[
\frac{E'}{E}=\frac{F'}{F}+\frac{Z_{\rm loc}'}{Z_{\rm loc}}.
\]
\end{lemma}

\begin{lemma}[Buffered local factor bound on $\partial B$]
\label{lem:Zloc-logder-collar}
Let $B=B(\alpha,m,\delta)$ be $\kappa$--admissible in the sense of Definition~\ref{def:collar-admissible}.
Then
\[
\sup_{v\in\partial B}\left|\frac{Z_{\rm loc}'(v)}{Z_{\rm loc}(v)}\right|
\le \frac{N_{\rm loc}(m)}{\kappa\,\delta},
\]
where $N_{\rm loc}(m)$ counts zeros of $E$ in the local window used to define $Z_{\rm loc}$, with multiplicity.
\end{lemma}


\begin{lemma}[Local log-derivative bound in $L^2(\partial B)$]
\label{lem:Zloc-L2-collar}
Let $B=B(\alpha,m,\delta)$ be $\kappa$--admissible (Definition~\ref{def:collar-admissible}), and let
$Z_{\rm loc}$ be the local factor with local zero-count $N_{\rm loc}(m)$ as in Section~\ref{sec:local-factor}.
Then
\[
\left\|\frac{Z'_{\rm loc}}{Z_{\rm loc}}\right\|_{L^2(\partial B)}
\le \frac{\sqrt{8}\,N_{\rm loc}(m)}{\kappa\,\delta^{1/2}}.
\]
More generally, for any $1\le r\le\infty$,
\[
\left\|\frac{Z'_{\rm loc}}{Z_{\rm loc}}\right\|_{L^r(\partial B)}
\le \frac{8^{1/r}N_{\rm loc}(m)}{\kappa\,\delta^{1-1/r}}.
\]
\end{lemma}

\begin{proof}
Lemma~\ref{lem:Zloc-logder-collar} gives $\|Z'_{\rm loc}/Z_{\rm loc}\|_{L^\infty(\partial B)}\le N_{\rm loc}(m)/(\kappa\delta)$.
Since $|\partial B|=8\delta$, we have $\|f\|_{L^r(\partial B)}\le |\partial B|^{1/r}\|f\|_{L^\infty(\partial B)}$ for every $1\le r\le\infty$,
which yields the stated bounds.
\end{proof}



\begin{lemma}[Explicit local window zero count]
\label{lem:Nloc-logm}
Let $N(T)$ denote the number of nontrivial zeros $\rho=\beta+i\gamma$ of $\zeta(s)$ with $0<\gamma\le T$,
counted with multiplicity.
Then for every $T\ge 5$,
\begin{equation}
\label{eq:two-unit-window}
N(T+1)-N(T-1)\le 1.01\log T + 17.
\end{equation}
Consequently, for every $m\ge 10$,
\begin{equation}
\label{eq:Nloc-explicit}
N_{\rm loc}(m)\le 1.01\log m + 17.
\end{equation}
\end{lemma}

\begin{proof}
By \cite[Theorem~1.1]{BellottiWongZeta2024}, for every $x\ge e$,
\[
\Bigl|\,N(x)-\frac{x}{2\pi}\log\!\Bigl(\frac{x}{2\pi e}\Bigr)\Bigr|
\le 0.10076\log x + 0.24460\log\log x + 8.08344.
\]
Let $M(x):=\frac{x}{2\pi}\log(\frac{x}{2\pi e})$, so $M'(x)=\frac{1}{2\pi}\log(\frac{x}{2\pi})$.
For $T\ge 5$ we have $\log(T\pm 1)\le \log(2T)$ and $\log\log x\le \log x$ for $x\ge e$, hence
\[
N(T+1)-N(T-1)
\le (M(T+1)-M(T-1)) + 2(0.10076+0.24460)\log(2T) + 2\cdot 8.08344.
\]
Moreover
\[
M(T+1)-M(T-1)=\int_{T-1}^{T+1}M'(x)\,dx
\le \int_{T-1}^{T+1}\frac{1}{2\pi}\log x\,dx
\le \frac{1}{\pi}\log(2T).
\]
Combining these bounds gives $N(T+1)-N(T-1)\le 1.00903\log T + 16.8663 \le 1.01\log T + 17$,
establishing \eqref{eq:two-unit-window}.
Finally, in width--2 one has $m=2T$.
The local window $|\ImPart\rho-m|\le 1$ corresponds to $|\gamma-T|\le 1/2$ in the $s$--plane, so
$N_{\rm loc}(m)=N(T+\tfrac12)-N(T-\tfrac12)\le N(T+1)-N(T-1)$, yielding \eqref{eq:Nloc-explicit}.
\end{proof}



\begin{corollary}[Outer-aligned upper envelope in residual+local form]
\label{cor:UE-residual-local}
Let $B$ be $\kappa$--admissible.
Assume the residual envelope bound of Lemma~\ref{lem:residual-envelope}, i.e.
\(\sup_{\partial B}|F'/F|\le L(m):=C_1\log m+C_2\).
Then
\[
\sum_{\pm}|W(v_\pm)-e^{i\varphi_0^\pm}|
\le 2C_{\rm up}\left(\delta L(m) + \frac{N_{\rm loc}(m)}{\kappa}\right)
\le 2C_{\rm up}\left(\delta L(m) + \frac{1.01\log m + 17}{\kappa}\right).
\]
\end{corollary}

\begin{remark}[UE gate = exponent budget at the local interface]
\label{rem:UE-gate}
Lemma~\ref{lem:upper-envelope} is the \emph{only} step in the envelope chain that generates a positive power
of $\delta$ in front of a boundary log-derivative endpoint.
Abstractly, suppose an upper-envelope mechanism yields, for some $p>0$,
\[
\sum_{\pm}\bigl|W(v_\pm)-e^{i\varphi_0^\pm}\bigr|
\le 2C_{\rm up}\,\delta^{p}\,\sup_{\partial B}\Bigl|\frac{E'}{E}\Bigr|,
\]
and suppose the collar/local split yields, for some $\theta>0$,
\[
\sup_{\partial B}\Bigl|\frac{E'}{E}\Bigr|
\le L(m)\ +\ \frac{N_{\rm loc}(m)}{\kappa\,\delta^{\theta}}.
\]
Then the local contribution in the envelope side scales as $\delta^{p-\theta}N_{\rm loc}(m)/\kappa$.
Under the nominal choice $\delta_0(m,\alpha)=\eta\alpha/(\log m)^2$ and the unconditional majorant
$N_{\rm loc}(m)\ll\log m$, uniform $\eta$--shrinking tail closure is possible only if
\[
p-\theta\ \ge\ \tfrac12
\]
(Theorem~\ref{thm:exponent-budget}).

In the \emph{proved} pointwise/sup architecture one has $p=1$ (Lemma~\ref{lem:upper-envelope}) and $\theta=1$ (Lemma~\ref{lem:Zloc-logder-collar}),
so $p-\theta=0$ and the local term is $\delta$--inert; $\eta$--shrinking cannot suppress it (Lemma~\ref{lem:UE-d1-obstruction}).
Moreover, within this same endpoint class, a strengthened exponent $p>1$ is impossible with shape--only constants
(Lemma~\ref{lem:UE-scaling-nogo}).
Thus the former $\eta$--absorption closure route based on the pointwise/sup UE endpoint is a formal NO--GO and is recorded as discarded
(Appendix~\ref{app:discarded}).
\end{remark}

\begin{theorem}[Exponent budget for $\eta$--shrinking under $\delta_0(m,\alpha)=\eta\alpha/(\log m)^2$]
\label{thm:exponent-budget}
Let $m\ge 10$, $\alpha\in(0,1]$ and $\eta\in(0,1]$, and set the nominal scale
\[
\delta_0(m,\alpha):=\frac{\eta\alpha}{(\log m)^2}.
\]
Assume that for all $0<\delta\le \delta_0(m,\alpha)$ one has:
\begin{enumerate}[leftmargin=1.5em]
\item[(UE$_p$)] (\emph{UE exponent}) for some $p>0$,
\[
\mathrm{UE}(\delta)\ \le\ 2C_{\rm up}\,\delta^{p}\,\sup_{\partial B}\Bigl|\frac{E'}{E}\Bigr|;
\]
\item[(COL$_\theta$)] (\emph{Collar/local exponent}) for some $\theta>0$,
\[
\sup_{\partial B}\Bigl|\frac{E'}{E}\Bigr|
\ \le\ L(m)\ +\ \frac{N_{\rm loc}(m)}{\kappa\,\delta^{\theta}},
\]
with fixed $\kappa\in(0,1/10)$;
\item[(GROW)] (\emph{Majorants}) $L(m)\le A_L\log m+B_L$ and $N_{\rm loc}(m)\le A_N\log m+B_N$ for all $m\ge 10$;
\item[(FORCE)] (\emph{Forcing side}) the forcing-vs-envelope tail inequality has a fixed positive forcing constant $c>0$ and only $\delta$--helpful subtractive terms on the RHS.
\end{enumerate}
Then at $\delta=\delta_0(m,\alpha)$ one has the explicit bound
\begin{equation}
\mathrm{UE}(\delta_0)\ \le\ 
2C_{\rm up}\Bigl(\delta_0^{p}L(m)\ +\ \delta_0^{p-\theta}\frac{N_{\rm loc}(m)}{\kappa}\Bigr).
\tag{BUDGET}
\end{equation}
Moreover, \emph{uniform tail closure by $\eta$--shrinking} (i.e.\ there exists $\eta_\star>0$ such that for every $\eta\le \eta_\star$ the tail inequality holds for all $m\ge 10$) is possible only if
\begin{equation}
p-\theta\ \ge\ \tfrac12.
\tag{B1}
\end{equation}
\end{theorem}

\begin{proof}
Insert (COL$_\theta$) into (UE$_p$) at $\delta=\delta_0$ to obtain (BUDGET).
At $\alpha=1$ one has $\delta_0(m,1)=\eta/(\log m)^2$, so the local term behaves as
\[
\delta_0^{p-\theta}N_{\rm loc}(m)\ \ll\ \Bigl(\frac{\eta}{(\log m)^2}\Bigr)^{p-\theta}\log m
=\eta^{p-\theta}(\log m)^{1-2(p-\theta)}.
\]
If $p-\theta<1/2$ then $1-2(p-\theta)>0$, so the local contribution grows without bound as $m\to\infty$,
while the forcing side tends to the fixed constant $c$ because all RHS corrections are $\delta$--helpful and vanish as $\delta_0\to 0$.
Hence uniform tail closure is impossible.
If $p-\theta\ge 1/2$ then the local contribution is uniformly bounded by $O(\eta^{p-\theta})$ and tends to $0$ as $\eta\downarrow 0$,
enabling uniform absorption once all constants are $\delta$--uniform.
\end{proof}



\begin{lemma}[$\eta$--absorption obstruction under the pointwise UE exponent $p=1$]
\label{lem:UE-d1-obstruction}
Assume the hypotheses of Corollary~\ref{cor:UE-residual-local}.
Then for every $\delta\le \delta_0(m,\alpha)=\eta\alpha/(\log m)^2$,
\[
\sum_{\pm}\bigl|W(v_\pm)-e^{i\varphi_0^\pm}\bigr|
\le 2C_{\rm up}\Bigl(\delta L(m)+\frac{N_{\rm loc}(m)}{\kappa}\Bigr).
\]
In particular, letting $\eta\downarrow 0$ (hence $\delta\downarrow 0$) only suppresses the residual term
$\delta L(m)$; the local term $N_{\rm loc}(m)/\kappa$ does \emph{not} decay with $\eta$.
Therefore any absorption-style closure that attempts to force the envelope side small by choosing $\eta$
must additionally verify a \emph{separate} inequality of the form
\[
\frac{2C_{\rm up}}{\kappa}\,N_{\rm loc}(m)\ <\ c
\]
at the relevant anchor height(s), where $c$ is the forcing constant in \eqref{eq:tail-ineq}.
\end{lemma}

\begin{lemma}[UE scaling NO--GO for pointwise/sup endpoints]
\label{lem:UE-scaling-nogo}
Assume an upper-envelope bound of the form
\[
\sum_{\pm}\bigl|W(v_\pm)-e^{i\varphi_0^\pm}\bigr|
\ \le\ 2C_{\rm up}\,\delta^{p}\,\sup_{\partial B}\Bigl|\frac{E'}{E}\Bigr|
\qquad (p>0),
\]
where the constant $C_{\rm up}$ depends only on the normalized shape (Lemma~\ref{lem:shape-only}) and is independent of $\delta$.
Then necessarily $p\le 1$.
In particular, no pointwise/sup envelope mechanism with shape--only constants can yield any exponent $p>1$.
\end{lemma}

\begin{proof}
Under the affine rescaling $T(v)=(v-(\alpha+im))/\delta$, the boundary $\partial B$ maps to the fixed square boundary $\partial Q$.
If $\widetilde E(z):=E(T^{-1}(z))$, then by the chain rule
\[
\frac{E'}{E}(T^{-1}(z))=\frac{1}{\delta}\,\frac{\widetilde E'(z)}{\widetilde E(z)}.
\]
Hence $\sup_{\partial B}|E'/E|=\delta^{-1}\sup_{\partial Q}|\widetilde E'/\widetilde E|$.
The left-hand side of the upper-envelope bound is dimensionless (it is a sum of moduli of complex numbers), and under the normalization it may be $O(1)$
for admissible configurations on the fixed shape.
Therefore the bound forces
\[
O(1)\ \le\ 2C_{\rm up}\,\delta^{p-1}\,\sup_{\partial Q}\Bigl|\frac{\widetilde E'}{\widetilde E}\Bigr|
\qquad\text{as }\delta\downarrow 0.
\]
Since the normalized endpoint $\sup_{\partial Q}|\widetilde E'/\widetilde E|$ is not forced to blow up as $\delta\downarrow 0$ (it depends only on the normalized data),
the factor $\delta^{p-1}$ cannot tend to $0$. Thus $p-1\le 0$, i.e.\ $p\le 1$.
\end{proof}



\begin{proof}
The displayed bound is exactly Corollary~\ref{cor:UE-residual-local} with the corrected UE exponent $p=1$.
As $\eta\to 0$ one has $\delta_0\to 0$ and hence $\delta L(m)\to 0$, while $N_{\rm loc}(m)/\kappa$ is unchanged.
Since the forcing lower bound in the tail inequality tends to $c$ as $\delta\downarrow 0$, the strict inequality
requires the stated necessary condition at the anchor.
\end{proof}


\subsection{Horizontal non-forcing budget in residual form}
\label{subsec:horizontal-budget}

\begin{definition}[Horizontal non-forcing phase budget]
\label{def:Delta-nonforce}
Let $B=B(\pm a,m,\delta)$ be an aligned box and let $F=E/Z_{\rm loc}$ be the residual factor.
Assume $F$ is holomorphic and zero-free on a neighborhood of $\partial B$.
Let $H_\pm$ denote the top and bottom edges of $\partial B$:
\[
H_+:=\{x+i(m+\delta):\ x\in[\pm a-\delta,\pm a+\delta]\},\qquad
H_-:=\{x+i(m-\delta):\ x\in[\pm a-\delta,\pm a+\delta]\}.
\]
Define
\[
\Delta_{\rm nonforce}(B)
:=
\int_{H_+}|\partial_s\arg F|\,ds + \int_{H_-}|\partial_s\arg F|\,ds.
\]
\end{definition}

\begin{lemma}[Horizontal budget (residual form; audit-grade)]
\label{lem:horizontal-budget}
In the setting of Definition~\ref{def:Delta-nonforce},
\[
\Delta_{\rm nonforce}(B)\le 4\delta\,\sup_{v\in\partial B}\left|\frac{F'(v)}{F(v)}\right|.
\]
Consequently, if $\sup_{\partial B}|F'/F|\le C_1\log m+C_2$, then
\[
\Delta_{\rm nonforce}(B)\le C_h''\,\delta\,(\log m+1),\qquad
C_h'':=4\max\{C_1,\,C_2\}.
\]
\end{lemma}

\begin{proof}
On either horizontal edge, $|\partial_s\arg F|\le |F'/F|$ pointwise.
Each edge has length $2\delta$, hence each integral is bounded by $2\delta\sup_{\partial B}|F'/F|$.
Summing top and bottom gives the first inequality, and the second follows from $\sup_{\partial B}|F'/F|\le C_1\log m+C_2\le \max\{C_1,C_2\}(\log m+1)$.
\end{proof}

\section{The explicit tail inequality (post-pivot)}
\label{sec:tail}
For $m\ge 10$ we use the growth surrogate
\[
L(m):=C_1\log m + C_2,
\]
with constants as in Lemma~\ref{lem:residual-envelope}.
For the local window term we use the explicit majorant from Lemma~\ref{lem:Nloc-logm}:
\[
N_{\rm up}(m):=1.01\log m + 17\ \ \text{so that}\ \ N_{\rm loc}(m)\le N_{\rm up}(m)\quad(m\ge 10).
\]

For a parameter $\eta\in(0,1)$ and a dial displacement $\alpha\in(0,1]$ define the \emph{nominal} scale
\[
\delta_0:=\delta_0(m,\alpha):=\frac{\eta\alpha}{(\log m)^2}.
\]
Fix a collar parameter $\kappa\in(0,1/10)$ as in Definition~\ref{def:collar-admissible}.
For each $(m,\alpha)$ we choose any scale $0<\delta\le\delta_0$ such that the aligned boxes
$B=B(\pm\alpha,m,\delta)$ are $\kappa$--admissible; existence is guaranteed by Lemma~\ref{lem:collar-existence}.
By Lemma~\ref{lem:delta-shrink-monotone}, shrinking $\delta$ only helps in the tail inequality, so it is safe to
treat $\delta_0$ as the worst-case scale in one-height reductions.

\begin{theorem}[Tail inequality (criterion form; pointwise UE exponent $p=1$)]
\label{thm:tail-inequality}
Fix $m\ge 10$ and $\eta\in(0,1)$.
Assume:
\begin{enumerate}[leftmargin=1.5em]
\item the forcing lemma producing the positive constant
\[
 c_0:=\frac{3\log 2}{8\pi},\qquad c:=\frac{3\log 2}{16},\qquad K_{\rm alloc}:=3+8\sqrt3;
\]
\item the residual envelope bound (Lemma~\ref{lem:residual-envelope}) providing $C_1,C_2$;
\item the audit-grade horizontal budget bound (Lemma~\ref{lem:horizontal-budget}), giving a constant
$C_h''$ independent of $(\alpha,m,\delta)$;
\item the explicit local window bound (Lemma~\ref{lem:Nloc-logm}) providing the majorant $N_{\rm up}(m)=1.01\log m+17$.
\end{enumerate}
Then for every $\alpha\in(0,1]$ and every $\kappa$--admissible aligned box $B=B(\pm\alpha,m,\delta)$,
absence of off--axis quartets at height $m$ follows from the strict inequality
\begin{equation}
\label{eq:tail-ineq}
2C_{\mathrm{up}}\Bigl(\delta L(m)\; +\; \frac{N_{\rm up}(m)}{\kappa}\Bigr)
\ <\
 c\ -\ \delta\Bigl(K_{\rm alloc}\,c_0\,L(m)+C_h''\,(\log m+1)\Bigr).
\end{equation}
\end{theorem}

\begin{proof}[Proof sketch / bookkeeping]
The forcing side is unchanged from v31. The only post-pivot modification is on the upper-envelope
side: Lemma~\ref{lem:upper-envelope} bounds dial deviation in terms of $\sup_{\partial B}|E'/E|$.
Applying the log-derivative split (Lemma~\ref{lem:logder-split}), the residual envelope for
$\sup_{\partial B}|F'/F|\le L(m)$ (Lemma~\ref{lem:residual-envelope}), and the collar bound
$\sup_{\partial B}|Z_{\rm loc}'/Z_{\rm loc}|\le N_{\rm loc}(m)/(\kappa\delta)$
(Lemma~\ref{lem:Zloc-logder-collar}) yields
\[
\sup_{\partial B}\Big|\frac{E'}{E}\Big|\le L(m)+\frac{N_{\rm loc}(m)}{\kappa\delta}
\le L(m)+\frac{N_{\rm up}(m)}{\kappa\delta}.
\]
Plugging this into Lemma~\ref{lem:upper-envelope} gives the left-hand side of
\eqref{eq:tail-ineq}.
The right-hand side is the forcing lower bound, with the horizontal non-forcing term bounded by
Lemma~\ref{lem:horizontal-budget}.
\end{proof}

\begin{lemma}[Monotonicity under $\delta$--shrinking]
\label{lem:delta-shrink-monotone}
Fix $m\ge 10$, $\alpha\in(0,1]$, and constants $C_{\rm up},\kappa,c,c_0,K_{\rm alloc},C_h'',C_1,C_2$.
Let $L(m)=C_1\log m + C_2$ and $N_{\rm up}(m)=1.01\log m +17$.
For $\delta\in(0,1]$ define
\[
\mathrm{LHS}(\delta):=
2C_{\mathrm{up}}\Bigl(\delta L(m)\; +\; \frac{N_{\rm up}(m)}{\kappa}\Bigr),
\qquad
\mathrm{RHS}(\delta):=
c\ -\ \delta\Bigl(K_{\rm alloc}\,c_0\,L(m)+C_h''\,(\log m+1)\Bigr).
\]
Then $\mathrm{LHS}(\delta)$ is (weakly) increasing in $\delta$ and $\mathrm{RHS}(\delta)$ is (weakly) decreasing.
Consequently, if $\mathrm{LHS}(\delta_0)<\mathrm{RHS}(\delta_0)$ for some $\delta_0\in(0,1]$, then
$\mathrm{LHS}(\delta)<\mathrm{RHS}(\delta)$ holds for every $\delta\in(0,\delta_0]$.
\end{lemma}

\begin{proof}
For $\delta>0$, the map $\delta\mapsto \delta L(m)$ is increasing and the term $N_{\rm up}(m)/\kappa$ is independent of $\delta$, hence $\mathrm{LHS}(\delta)$ is (weakly) increasing.
The bracketed factor in $\mathrm{RHS}(\delta)$ is nonnegative and independent of $\delta$, so $\mathrm{RHS}(\delta)$ decreases linearly in $\delta$.
\end{proof}



\begin{lemma}[Worst case in $\alpha$ is $\alpha=1$ at the nominal scale]
\label{lem:worst-alpha}
Fix $m\ge 10$ and $\eta\in(0,1)$. Define the nominal scale $\delta_0(m,\alpha)=\eta\alpha/(\log m)^2$.
Consider the tail inequality \eqref{eq:tail-ineq} evaluated at $\delta=\delta_0(m,\alpha)$.
Then the left-hand side is (weakly) \emph{increasing} in $\alpha\in(0,1]$, while the right-hand side is (weakly)
\emph{decreasing}.
Therefore it suffices to verify \eqref{eq:tail-ineq} at $\alpha=1$ and $\delta=\delta_0(m,1)$.
If one later shrinks $\delta\le\delta_0(m,\alpha)$ to enforce $\kappa$--admissibility, the inequality only becomes easier
(Lemma~\ref{lem:delta-shrink-monotone}).
\end{lemma}

\begin{proof}
With $\delta=\delta_0(m,\alpha)=\eta\alpha/(\log m)^2$, the only $\alpha$-dependence in the left-hand side is through the factor $\delta L(m)$, which is increasing in $\alpha$,
so the left-hand side increases.
The right-hand side equals $c-\delta\cdot\Xi(m)$ for a nonnegative factor $\Xi(m)$ independent of $\alpha$, hence it decreases.
\end{proof}


\begin{remark}[No one-height reduction in $m$ under the pointwise UE exponent $p=1$]
\label{rem:no-one-height}
In v33, the (claimed) $\delta^{3/2}$ prefactor in Lemma~\ref{lem:upper-envelope} made the local contribution
scale like $\delta^{1/2}N_{\rm up}(m)$ at the nominal choice $\delta_0(m,\alpha)=\eta\alpha/(\log m)^2$,
leading to an expression essentially independent of $m$ and enabling a one-height reduction.
After the UE--Gate audit, Lemma~\ref{lem:upper-envelope} provides only the pointwise exponent $p=1$,
so the tail left-hand side contains the $\delta$--inert term $(2C_{\rm up}/\kappa)\,N_{\rm up}(m)$.
With the explicit majorant $N_{\rm up}(m)=1.01\log m+17$, this term is \emph{increasing} in $m$.
Therefore a one-height reduction in $m$ is not available under the current pointwise envelope mechanism:
the tail criterion must be controlled as a family in $m$, or the UE--Gate must be cleared by a strengthened
envelope mechanism (Remark~\ref{rem:UE-gate}).
\end{remark}

\section{GEO--C4 frontier: hinge-centered harmonic endpoint (active)}
\label{sec:S5-frontier}

% ============================================================
% v40: defect endpoint primitives (Q_a, L_a) + local cancellation + ML-\(\Delta a\) redesign
% ============================================================

\subsection{Defect quotient primitives and cancellation mechanism (v40)}
\label{subsec:defect-primitives}

\begin{definition}[Defect quotient and defect log-derivative]
\label{def:defect-quotient}
Fix $a\in(0,1)$ and let $E$ be the even entire width--2 completion (Section~\ref{sec:width2}).
Define the \emph{defect quotient} and its logarithmic derivative by
\[
\mathcal Q_a(v)\ :=\ \frac{E(v+a)}{E(v-a)},\qquad
\mathcal L_a(v)\ :=\ \frac{\mathcal Q_a'(v)}{\mathcal Q_a(v)}
\ =\ \frac{E'}{E}(v+a)-\frac{E'}{E}(v-a),
\]
whenever the expressions are defined.  The function $\mathcal L_a$ is holomorphic on any domain
where $E(v\pm a)\neq 0$.
\end{definition}

\begin{definition}[Defect phase endpoint on a $\kappa$--admissible box]
\label{def:defect-endpoint}
Let $B=B(\alpha,m,\delta)$ be a $\kappa$--admissible aligned box and let $\partial B_{\kappa/2}$
denote its buffered contour as in Definition~\ref{def:Db-tilde-phase}.
Define the \emph{defect phase endpoint} by
\[
\Phi^{\rm def}_B(a)\ :=\
\max_{I\in \mathrm{Sides}(\partial B_{\kappa/2})}\ \left|\Im\int_I \mathcal L_a(v)\,dv\right|.
\]
(Here $\mathrm{Sides}(\partial B_{\kappa/2})$ denotes the four oriented sides of the rectangle.)
\end{definition}

\begin{lemma}[Side-length ceiling for the defect phase endpoint]\label{lem:defect-p-ceiling}
Fix \(a\in(0,1]\) and let \(B=B(\alpha,m,\delta)\) be a \(\kappa\)-admissible aligned box with buffered contour \(\partial B_{\kappa/2}\).
Assume \(\mathcal L_a\) is holomorphic on an open neighborhood of \(\partial B_{\kappa/2}\).
Then
\[
  \Phi_B^{\rm def}(a)\ \le\ C_{\rm geom}\,\delta\cdot \sup_{v\in\partial B_{\kappa/2}}|\mathcal L_a(v)|,
\]
where \(C_{\rm geom}>0\) is an absolute rectangle-shape constant.
In particular, any estimate of the form \(\Phi_B^{\rm def}(a)\ll \delta^p(\cdots)\) obtained solely from
\(\delta\)-uniform pointwise bounds on \(\sup_{\partial B_{\kappa/2}}|\mathcal L_a|\) cannot have \(p>1\).
\end{lemma}

\begin{proof}
By Definition~\ref{def:defect-endpoint} and the triangle inequality,
\[
\left|\Im\int_I \mathcal L_a(v)\,dv\right|
\le \int_I |\mathcal L_a(v)|\,|dv|
\le |I|\cdot \sup_{v\in\partial B_{\kappa/2}}|\mathcal L_a(v)|.
\]
Each side length satisfies \(|I|\le C_{\rm geom}\,\delta\) for an absolute constant depending only on the rectangle shape (and the fixed buffering policy), hence the claim.
\end{proof}

\begin{definition}[Two-sided shift-difference defect operator]\label{def:two-sided-shift-diff}
Let \(E\) be the even entire completion in the \(v\)-plane, and define the defect quotient and defect log-derivative
\[
\mathcal Q_a(v):=\frac{E(v+a)}{E(v-a)},\qquad
\mathcal L_a(v):=\frac{\mathcal Q_a'(v)}{\mathcal Q_a(v)}
=\frac{E'}{E}(v+a)-\frac{E'}{E}(v-a).
\]
For a shift step \(h>0\), define the two-sided shift-difference operator
\[
\mathcal D_{a,h}(v):=\mathcal L_{a+h}(v)-\mathcal L_{a-h}(v).
\]
Equivalently,
\[
\mathcal D_{a,h}(v)
=
\Big(\frac{E'}{E}(v+a+h)-\frac{E'}{E}(v+a-h)\Big)
-\Big(\frac{E'}{E}(v-a+h)-\frac{E'}{E}(v-a-h)\Big).
\]
\end{definition}

\begin{definition}[Two-sided shift-difference phase endpoint]\label{def:two-sided-endpoint}
Fix \(\kappa\in(0,1/10)\). For a \(\kappa\)-admissible aligned box \(B=B(\alpha,m,\delta)\) and parameters \((a,h)\), define
\[
\Phi^{(2\mathrm{s})}_B(a;h)
:=\max_{I\in\mathrm{Sides}(\partial B_{\kappa/2})}
\left|\Im\int_I \mathcal D_{a,h}(v)\,dv\right|.
\]
In the nominal coupling used in this program we take \(h=\delta\) and \(\delta=\delta_0(m,a):=\eta a/(\log m)^2\).
\end{definition}

\begin{lemma}[Aligned-box forcing NO-GO for the two-sided endpoint]
\label{lem:deltaa-alignedbox-nogo}
Assume $E$ has a quartet at $\{\pm a\pm im\}$ with $a>0$ and fix $\kappa\in(0,1/10)$.
Let $B=B(a,m,\delta)$ be the aligned box at the pole height and suppose $B$ is $\kappa$--admissible.
If $0<h\le \delta\le a/4$, then in the toy quartet model one has
\[
\Phi^{(2\mathrm{s})}_B(a;h)\ \le\ C\,\frac{\delta h}{a^2},
\]
for an absolute constant $C$.
In particular at the nominal coupling $h=\delta=\eta a/(\log m)^2$ one gets
$\Phi^{(2\mathrm{s})}_B(a;h)\ll \eta^2/(\log m)^4\to 0$ as $m\to\infty$.
\smallskip
\noindent\emph{Therefore any viable $\Delta a$ forcing mechanism must change the witness family and/or the coupling of $h$ to $\delta$.}
\end{lemma}



\begin{lemma}[Local defect cancellation for a forced top pair]
\label{lem:defect-cancellation}
Assume $E$ has a nontrivial quartet at height $m$ with displacement $a>0$, so that
$E(\pm a \pm i m)=0$ (with multiplicity $r\ge 1$ at each of $\pm a+i m$).
Let $B=B(0,m,\delta)$ with $0<\delta\le a/4$, and assume $B$ is $\kappa$--admissible.
Then $\mathcal Q_a$ has a removable singularity at $v=i m$, $\mathcal L_a$ is holomorphic on $B_{\kappa/2}$,
and the pure--pair contribution to $\Phi^{\rm def}_B(a)$ is $O(r\,\delta/a)$.
More precisely, writing
\[
\frac{E'}{E}(v)=\frac{r}{v-(a+i m)}+\frac{r}{v-(-a+i m)}+H(v),
\]
with $H$ holomorphic on $B_{\kappa/2}$, one has on $\partial B_{\kappa/2}$:
\[
\mathcal L_a(v)= r\Bigl(\frac{1}{v-(2a+i m)}-\frac{1}{v-(-2a+i m)}\Bigr)\ +\ \bigl(H(v+a)-H(v-a)\bigr).
\]
Consequently,
\[
\max_{v\in \partial B_{\kappa/2}}
\left|r\Bigl(\frac{1}{v-(2a+i m)}-\frac{1}{v-(-2a+i m)}\Bigr)\right|
\ \le\ \frac{C\,r}{a},
\qquad
\Rightarrow\qquad
\Phi^{\rm def}_B(a)\ \le\ C\,r\,\frac{\delta}{a}\ +\ \delta\,\|H(\cdot+a)-H(\cdot-a)\|_{L^\infty(\partial B_{\kappa/2})}.
\]
\end{lemma}

\begin{proof}
Factor $E(v)=(v-(a+i m))^r(v-(-a+i m))^r\cdot \widetilde E(v)$ locally near $v=i m$ with $\widetilde E$
holomorphic and nonzero on $B_{\kappa/2}$ (possible since $B$ is $\kappa$--admissible and $\delta\le a/4$ keeps the other zeros away).
Then $\mathcal Q_a(v)=E(v+a)/E(v-a)$ has the same power of $(v-i m)^r$ in numerator and denominator, so $v=i m$ is removable and
$\mathcal L_a$ is holomorphic on $B_{\kappa/2}$.

For the displayed decomposition, write $\frac{E'}{E}(v)=\sum_{\rho\in Z(E)}\frac{m(\rho)}{v-\rho}$ and isolate the
two terms at $\rho=\pm a+i m$, absorbing all other contributions into a holomorphic $H$ on $B_{\kappa/2}$.
Shift by $\pm a$ and subtract to obtain the identity for $\mathcal L_a(v)$.
Finally,
\[
\frac{1}{v-(2a+i m)}-\frac{1}{v-(-2a+i m)}
=\frac{4a}{(v-(2a+i m))(v-(-2a+i m))},
\]
and on $\partial B_{\kappa/2}$ we have $|v-(\pm 2a+i m)|\ge a$ when $\delta\le a/4$, giving the $O(r/a)$ bound.
The endpoint bound follows by integrating along a side of length $O(\delta)$ and taking the maximum over the four sides.
\end{proof}

\begin{lemma}[Shift stability of the defect endpoint]
\label{lem:defect-shift-stability}
Let $C$ be any rectifiable contour such that $E(v\pm a)\neq 0$ for all $v\in C$.
Then
\[
\sup_{v\in C}|\mathcal L_a(v)|
\le
\sup_{w\in C+a}\Bigl|\frac{E'(w)}{E(w)}\Bigr|
+\sup_{w\in C-a}\Bigl|\frac{E'(w)}{E(w)}\Bigr|.
\]
In particular, any collar bound for $E'/E$ on buffered contours transfers verbatim to $\mathcal L_a$
on the corresponding shifted buffered contours.
\end{lemma}

\begin{proof}
This is immediate from Definition~\ref{def:defect-quotient} and the triangle inequality.
\end{proof}

\begin{definition}[Horizontal resonance sum (local window)]
\label{def:resonance-sum}
For $a\in(0,1]$ and $m\ge 10$, define the \emph{horizontal resonance sum}
\[
\mathcal R_a(m)\ :=\ \sum_{\substack{\rho:\ E(\rho)=0\\ |\Im(\rho)-m|\le 1}}
\frac{1}{|\Re(\rho)-a|+a},
\]
where each zero is counted with multiplicity.  This sum is finite and satisfies
$\mathcal R_a(m)\le \frac{1}{a}\,N_{\rm loc}(m)$.
\end{definition}

\begin{remark}[Archived benchmark: defect UE target (S5$^{\rm def}$)]
The bound below was the \emph{v40--v41} target for the \emph{centered defect endpoint} $\Phi^{\rm def}_B(a)$ built from $\mathcal L_a$.
It is retained only as a comparison benchmark and as a warning label: the centered defect endpoint suffers an $O(\delta/a)$ cancellation and a $\delta$-inert resonance obstruction, so it is \emph{not} load-bearing in the active GEO--C4 chain (v43).

\smallskip
Formally, the discarded target inequality was of the schematic form
\[
\Phi^{\rm def}_{B(0,m,\delta)}(a)\ \le\ C\,\eta
\quad\text{at}\quad
\delta=\eta\,\frac{a}{(\log m)^2},
\]
which would contradict any absolute forcing lower bound for $\Phi^{\rm def}$.
In v43 we replace $\Phi^{\rm def}$ by the hinge-circle harmonic endpoint $\Phi^\star$ (Box~\ref{box:geo-c4-v43}).
\end{remark}

\begin{definition}[$\delta$-aware resonance sum]\label{def:resonance-sum-delta}
For $a\in(0,1]$, $m\ge 10$, and $0<\delta\le 1$, define the \emph{$\delta$-aware resonance sum}
\[
\mathcal R_{a,\delta}(m)\ :=\ \sum_{\substack{\rho:\ E(\rho)=0\\ |\Im(\rho)-m|\le 1}}
\frac{1}{|\Re(\rho)-a|+\delta},
\]
where each zero is counted with multiplicity.  This sum is finite and satisfies
\(
\mathcal R_{a,\delta}(m)\le \delta^{-1}N_{\rm loc}(m).
\)
\end{definition}

\begin{remark}[$\delta$-aware defect UE target (archived benchmark)]
\label{rem:defect-UE-target-delta}
A $\delta$-uniform defect UE bound that explicitly accounts for resonance should be formulated in terms of
$\mathcal R_{a,\delta}(m)$ rather than the $\delta$-blind sum $\mathcal R_a(m)$.
A schematic form is
\[
\Phi^{\rm def}_B(a)\ \le\ C_0\,\delta\,\log m\ +\ C_1\,\delta\,a\,\mathcal R_{a,\delta}(m),
\qquad
0<\delta\le \delta_0(m,a)=\eta\,\frac{a}{(\log m)^2}.
\]
This inequality is \emph{not} claimed here; it is recorded as the correct resonance-aware target should one revisit
the defect endpoint class in future work.
\end{remark}

\begin{definition}[Near-resonance count]\label{def:near-resonance-count}
For $a\in(0,1]$, $m\ge 10$, and $0<\delta\le 1$, define the near-resonance count
\[
N_{\rm near}(m;a,\delta)\ :=\ \#\{\rho:\ E(\rho)=0,\ |\Im(\rho)-m|\le 1,\ |\Re(\rho)-a|\le \delta\},
\]
counted with multiplicity.
\end{definition}

\begin{remark}[$\mathcal R_a(m)$ is $\delta$-blind]
\label{rem:Ra-deltablind}
The $\delta$-blind sum $\mathcal R_a(m)$ (Definition~\ref{def:resonance-sum}) cannot rule out near-resonance:
one may have $N_{\rm near}(m;a,\delta)\ge 1$ with $\delta\ll a$ while still having $\mathcal R_a(m)\asymp a^{-1}$.
By contrast, $\mathcal R_{a,\delta}(m)\gtrsim \delta^{-1}$ whenever $N_{\rm near}(m;a,\delta)\ge 1$.
Thus any $\delta$-uniform local analysis must track $\delta$-aware resonance (either via $\mathcal R_{a,\delta}$ or via $N_{\rm near}$).
\end{remark}

\begin{lemma}[NO--GO: near-resonant quartets can make defect endpoints $\delta$--inert]
\label{lem:defect-resonance-nogo}
Fix $a\in(0,1)$, $m>0$, and $0<\varepsilon<a/2$.  Define the even polynomial
\[
E_{\varepsilon}(v):=\prod_{\sigma\in\{\pm1\}}\prod_{\tau\in\{\pm1\}}
\bigl(v-\sigma(a+i\tau m)\bigr)\cdot
\bigl(v-\sigma((a-\varepsilon)+i\tau m)\bigr),
\]
and form $\mathcal Q_a,\mathcal L_a$ as in Definition~\ref{def:defect-quotient}.
Let $B=B(0,m,\delta)$ with $\delta\in[\varepsilon/2,2\varepsilon]$ and take $\kappa=1/10$.
Then $B$ is $\kappa$--admissible (for $\delta\ll a$), but the defect endpoint satisfies
\[
\Phi^{\rm def}_B(a)\ \ge\ c_0
\]
for an absolute constant $c_0>0$ independent of $\delta$ and $\varepsilon$.
In particular, $\Phi^{\rm def}_B(a)$ need not shrink as $\delta\to 0$ unless horizontal resonance is controlled.
\end{lemma}

\begin{proof}[Proof sketch]
Write $w=v-i m$.  A direct computation shows that $\mathcal Q_a(v)$ contains the factor
\[
g_{\varepsilon}(w):=\frac{w+\varepsilon}{w-\varepsilon},
\]
coming from the second quartet at real part $a-\varepsilon$:
indeed $E_\varepsilon(v+a)$ vanishes at $v=i m-\varepsilon$ and $E_\varepsilon(v-a)$ vanishes at $v=i m+\varepsilon$.
Hence $\mathcal Q_a$ has a zero at $w=-\varepsilon$ and a pole at $w=\varepsilon$.

Consider the right vertical side of $\partial B_{\kappa/2}$, parameterized as $w=\delta+i t$ with $t\in[-\delta,\delta]$.
On this side,
\[
\arg g_\varepsilon(\delta+i t)=\arg(\delta+\varepsilon+i t)-\arg(\delta-\varepsilon+i t),
\]
so the phase increment along the side is
\[
\Delta_t\arg g_\varepsilon=\Bigl[\arctan\!\Bigl(\frac{t}{\delta+\varepsilon}\Bigr)
-\arctan\!\Bigl(\frac{t}{\delta-\varepsilon}\Bigr)\Bigr]_{t=-\delta}^{t=\delta}
=2\arctan\!\Bigl(\frac{\delta}{\delta+\varepsilon}\Bigr)-2\arctan\!\Bigl(\frac{\delta}{\delta-\varepsilon}\Bigr).
\]
If $\delta\in[\varepsilon/2,2\varepsilon]$, then $\delta-\varepsilon$ has magnitude $\ll \delta$ and the second arctangent
is bounded away from $0$, forcing $|\Delta_t\arg g_\varepsilon|\ge c_0$ for an absolute $c_0>0$.
Since $\Delta\arg g_\varepsilon$ is an oriented side phase increment, this lower bound implies
$\Phi^{\rm def}_B(a)\ge c_0$ (up to $O(\delta/a)$ terms from the far factors).
\end{proof}




% ============================================================
% ARCHIVED (v43): former missing lever box for S5' defect endpoints
% ============================================================


\begin{lemma}[NO--GO: no $\delta$--uniform transfer to the centered defect box]\label{lem:ML1-samebox-nogo}
Fix $\kappa\in(0,1/10)$ and $a\in(0,1)$.  Let $B=B(\pm a,m,\delta)$ be an aligned box at height $m$ and let
$\widehat B=B(0,m,\delta)$ be the centered box of the same height and scale.
Assume both boxes are $\kappa$--admissible and that $E$ has a quartet at height $m$ with tilt $a$, so that
$E(\pm a\pm i m)=0$.

Then there is \emph{no} constant $C_{\rm tr}$ independent of $\delta$ such that the transfer inequality
\[
\widetilde D_B(W)\ \le\ C_{\rm tr}\,\Phi^{\rm def}_{\widehat B}(a)
\]
holds uniformly as $\delta\downarrow 0$ for this box family.
\end{lemma}

\begin{proof}
By Lemma~\ref{lem:phase-forcing-argprinciple}, the interior zero of $W$ in $B_{\kappa/2}$ forces
$\widetilde D_B(W)\ge \pi/2$ on the aligned box, uniformly in $\delta$.
On the other hand, Lemma~\ref{lem:defect-cancellation} shows that on the centered box $\widehat B=B(0,m,\delta)$
the defect endpoint may satisfy $\Phi^{\rm def}_{\widehat B}(a)=O(\delta/a)$ as $\delta\to 0$ (even for a single quartet).
Thus any inequality of the displayed form would force $\pi/2\le C_{\rm tr}\,O(\delta/a)$, which fails for $\delta\downarrow 0$.
\end{proof}

\begin{remark}[Consequence for S5 endpoints]\label{rem:ml1-transfer-note}
Lemma~\ref{lem:ML1-samebox-nogo} is the decisive obstruction to any v39-style strategy that tries to transfer
aligned-box forcing to a centered defect box at the \emph{same} scale $\delta$.
Any future closure attempt must either (i) use an endpoint that is forceable on the aligned box itself,
or (ii) introduce genuinely new structure that avoids the centered cancellation mechanism.
\end{remark}

\begin{lemma}[NO--GO: defect-box pole-winding cannot substitute for transfer]\label{lem:defectbox-nogo-ML1}
Fix $\kappa\in(0,1/10)$ and $a\in(0,1)$.  Let $\widehat B=B(2a,m,\delta)$ be the defect box that contains the pole $v=2a+i m$
in the toy configuration of Lemma~\ref{lem:defect-cancellation}, and assume $\widehat B$ is $\kappa$--admissible.

If $E$ has a quartet at height $m$ with tilt $a$, then for all sufficiently small $\delta\ll a$,
\[
\Phi^{\rm def}_{\widehat B}(a)\ \ge\ \frac{\pi}{2},
\]
independently of $\delta$.
Consequently, no inequality of the form $\Phi^{\rm def}_{\widehat B}(a)\le C\,\delta^p(\log m)^q$ with $p>0$ and $C$
independent of $\delta$ can hold uniformly as $\delta\to 0$ on this defect-box family.
\end{lemma}

\begin{proof}
Since $E(a+i m)=0$, the denominator $E(v-a)$ vanishes at $v_0=2a+i m$, so $\mathcal Q_a$ has a pole at $v_0$.
Under $\kappa$--admissibility, $\mathcal Q_a$ is meromorphic in a neighborhood of $\partial\widehat B_{\kappa/2}$ with exactly one
pole and no zeros/poles on the contour. The argument principle gives total phase change $2\pi$ in magnitude around
$\partial\widehat B_{\kappa/2}$. Since $\partial\widehat B_{\kappa/2}$ is the concatenation of four oriented sides,
at least one side has phase increment magnitude at least $\pi/2$. By definition of $\Phi^{\rm def}_{\widehat B}(a)$
as the max side increment, $\Phi^{\rm def}_{\widehat B}(a)\ge\pi/2$.
The incompatibility with any $p>0$ $\delta$--gain is immediate.
\end{proof}


% === BEGIN: GEO-C4 closure box (v43) ===
\begin{center}
\fbox{%
\begin{minipage}{0.95\textwidth}
\textbf{Active closure lever (v43): GEO--C4 hinge--circle $k=2$ harmonic endpoint.}\label{box:geo-c4-v43}

\smallskip
\emph{Witness geometry (hinge circle).}
Fix a height $m>0$, a candidate tilt $a\in(0,1)$, and a scale $\delta>0$.  Let
\[
v(\theta)= i m+\delta e^{i\theta},\qquad \theta\in[0,2\pi],
\]
and set the coupling $h=\kappa\delta$ with a fixed $\kappa\in(0,1)$.

\smallskip
\emph{GEO--C4 second--difference log--derivative.}
Define for $t>0$
\[
\mathcal L_t(v):=\frac{E'}{E}(v+t)-\frac{E'}{E}(v-t),
\qquad
\mathcal D_{a,h}(v):=\mathcal L_{a+h}(v)-\mathcal L_{a-h}(v),
\]
and the phase signal on the hinge circle
\[
\psi_{a,h}(\theta):=\Im\big(\mathcal D_{a,h}(v(\theta))\big).
\]
Let $P_2$ be the orthogonal projection onto $\mathrm{span}\{\cos(2\theta),\sin(2\theta)\}$ and set
\[
\Phi^\star(m,a,\delta,h):=\frac{\delta^2}{h}\,\|P_2\psi_{a,h}\|_{L^2([0,2\pi])}.
\]

\smallskip
\emph{FORCE.}  If there is an off--axis quartet at height $m$ with tilt $a>0$ (i.e. $E(\pm a\pm i m)=0$), then (under shift--admissibility / buffering) one has a uniform forcing lower bound
\[
\Phi^\star(m,a,\delta,h)\ge c_0(\kappa)>0
\quad\text{(Lemmas \ref{lem:geo-c4-toy-force} and \ref{lem:geo-c4-force-stable}).}
\]

\smallskip
\emph{UE--REDUCE.}  For every shift--admissible hinge circle,
\[
\Phi^\star(m,a,\delta,h)\ \le\ \frac{\delta^2}{\sqrt{\pi}\,h}\int_0^{2\pi}\left|\mathcal D_{a,h}(v(\theta))\right|\,d\theta
\quad\text{(Lemma \ref{lem:geo-c4-ue-reduction}).}
\]

\smallskip
\emph{Single active analytic obligation (UE--INPUT).}  Prove the $H^1$/boundary--$L^1$ control
\[
\int_0^{2\pi}\left|\mathcal D_{a,h}(v(\theta))\right|\,d\theta
\ \le\ C\,h\,\frac{(\log(m+3))^{C'}}{a^{2}}
\qquad\text{at the nominal policy }\delta=\eta\frac{a}{(\log(m+3))^2},\ h=\kappa\delta,
\]
as stated in Box \ref{box:ue-input-v43}.  Combined with UE--REDUCE this yields
\[
\Phi^\star(m,a,\delta,h)\ \le\ \frac{C}{\sqrt{\pi}}\,
\left(\frac{\delta}{a}\right)^2(\log(m+3))^{C'}
\ =\ \frac{C}{\sqrt{\pi}}\,
\eta^2(\log(m+3))^{C'-4}.
\]
Thus for any exponent budget $C'<4$ (or for $C'=4$ with $\eta$ chosen sufficiently small), the UE upper bound contradicts FORCE, ruling out $a>0$ at that height.  Since $m$ is arbitrary, this closes PHU and hence RH.

\end{minipage}}
\end{center}
% === END: GEO-C4 closure box (v43) ===


\subsection{GEO--C4 endpoint: toy forcing, stability, and UE reduction}\label{sec:geo-c4}

The previous S5$'$ defect endpoints are now \emph{archived}; the active v43 endpoint is the hinge--circle harmonic functional $\Phi^\star$ from Box~\ref{box:geo-c4-v43}.  We record here (i) a proof--grade toy forcing computation, (ii) a stability lemma showing the forcing persists for the true completed object after monotone admissibility shrink, and (iii) an explicit reduction of the needed UE bound to a single derivative--field estimate (UE-INPUT).

\subsubsection{Shift-admissibility on hinge circles}

\begin{definition}[Shift-admissible hinge circle]\label{def:shift-admissible-hinge}
Fix $(m,a,\delta,h)$ with $0<h<\delta$.  We say the hinge circle $C_{m,\delta}$ is \emph{shift-admissible at $(a,h)$} if
\[
E\bigl(v(\theta)\pm(a\pm h)\bigr)\neq 0\qquad\text{for all }\theta\in[0,2\pi],
\]
so that $\mathcal D_{a,h}(v(\theta))$ is well-defined and continuous on $[0,2\pi]$.
We say it is \emph{$\mathrm{buf}$--admissible} if, additionally,
\[
\min_{\theta}\min_{\pm,\pm}\ \mathrm{dist}\Bigl(v(\theta)\pm(a\pm h),\,Z(E)\Bigr)\ \ge\ \mathrm{buf}\cdot\delta,
\]
for some fixed $\mathrm{buf}\in(0,1)$.
\end{definition}

\begin{remark}[Monotone admissibility shrink]\label{rem:monotone-shrink}
Zeros of an entire function are isolated.  Hence, if a fixed quartet $\{\pm a\pm i m\}\subset Z(E)$ exists, then by shrinking $\delta$ one can always arrange
$\mathrm{buf}$--admissibility for a hinge circle centered at $i m$ with coupling $h=\kappa\delta$ ($\kappa\in(0,1)$ fixed).
In the active closure chain we always allow this shrink; UE bounds are required only in a form monotone in $\delta$ (``smaller $\delta$ makes UE easier'').
\end{remark}

\subsubsection{Toy forcing computation (one quartet)}

\begin{lemma}[Toy forcing for the $k=2$ harmonic endpoint]\label{lem:geo-c4-toy-force}
Let
\[
E_{\rm toy}(v):=\prod_{\sigma=\pm1}\prod_{\tau=\pm1}\bigl(v-\sigma a-i\tau m\bigr)
=(v^2-(a+i m)^2)(v^2-(a-i m)^2),
\]
and define $\mathcal L_t,\mathcal D_{a,h}$ and $\Phi^\star$ as in Box~\ref{box:geo-c4-v43}.  Assume $0<h<\delta$ and set $v(\theta)=i m+\delta e^{i\theta}$.
Then the induced signal $\psi_{a,h}(\theta)=\Im(\mathcal D_{a,h}(v(\theta)))$ has
\[
A_c:=\int_0^{2\pi}\psi_{a,h}(\theta)\cos(2\theta)\,d\theta=0,
\qquad
A_s:=\int_0^{2\pi}\psi_{a,h}(\theta)\sin(2\theta)\,d\theta=\frac{4\pi h}{\delta^2},
\]
and therefore
\[
\bigl\|P_2\psi_{a,h}\bigr\|_{L^2([0,2\pi])}=\frac{|A_s|}{\sqrt{\pi}}=\frac{4\sqrt{\pi}\,h}{\delta^2},
\qquad
\boxed{\ \Phi^\star(m,a,\delta,h)=4\sqrt{\pi}\ }.
\]
\end{lemma}

\begin{proof}
Write $F(v):=E'_{\rm toy}(v)/E_{\rm toy}(v)=\sum_{\rho\in\{\pm a\pm i m\}}\frac{1}{v-\rho}$.
Fix $v=i m+u$.  The two \emph{top} zeros $\rho=\pm a+i m$ contribute
\[
F(v+a\pm h)\supset \frac{1}{u\pm h},
\qquad
F(v-a\pm h)\supset \frac{1}{u\mp h},
\]
hence (by the definition of $\mathcal D_{a,h}$)
\[
\mathcal D_{a,h}(i m+u)
=
\Big(\frac{1}{u+h}-\frac{1}{u-h}\Big)
-\Big(\frac{1}{u-h}-\frac{1}{u+h}\Big)
\ +\ (\text{terms analytic in a neighborhood of }u=0),
\]
so the singular part is exactly
\[
\mathcal D^{\rm sing}_{a,h}(i m+u)=\frac{-4h}{u^2-h^2}.
\]
On the hinge circle $u=\delta e^{i\theta}$, set $r:=h/\delta\in(0,1)$ and rewrite
\[
\mathcal D^{\rm sing}_{a,h}(v(\theta))
=\frac{-4h}{\delta^2 e^{2i\theta}-h^2}
=\frac{-4h}{\delta^2}\cdot \frac{1}{e^{2i\theta}-r^2}
=\frac{-4h}{\delta^2}\,e^{-2i\theta}\sum_{n\ge 0}r^{2n}e^{-2in\theta},
\]
where we used the geometric series $(1-r^2e^{-2i\theta})^{-1}=\sum_{n\ge0}r^{2n}e^{-2in\theta}$ (valid since $r<1$).
Taking imaginary parts gives the exact Fourier series
\[
\psi^{\rm sing}_{a,h}(\theta)=\Im\big(\mathcal D^{\rm sing}_{a,h}(v(\theta))\big)
=\frac{4h}{\delta^2}\sum_{k\ge 1}r^{2(k-1)}\sin(2k\theta).
\]
In particular, the $k=1$ term shows that the $\sin(2\theta)$ coefficient equals $4h/\delta^2$, and there is no $\cos(2\theta)$ term.  Hence
\[
A_s=\int_0^{2\pi}\psi^{\rm sing}_{a,h}(\theta)\sin(2\theta)\,d\theta
=\frac{4h}{\delta^2}\int_0^{2\pi}\sin^2(2\theta)\,d\theta=\frac{4h}{\delta^2}\cdot\pi=\frac{4\pi h}{\delta^2},
\]
and $A_c=0$.
Since $P_2$ only depends on $(A_c,A_s)$, this yields the claimed $\|P_2\psi\|_{L^2}$ and therefore $\Phi^\star=4\sqrt{\pi}$.
\end{proof}

\subsubsection{Forcing for the true completed object: stability under analytic remainders}

\begin{lemma}[Local forcing is stable after admissibility shrink]\label{lem:geo-c4-force-stable}
Let $E$ be the completed even entire object in the $v$--plane.  Fix a height $m>0$ and suppose $E(\pm a\pm i m)=0$ for some $a>0$.
Fix $\kappa\in(0,1)$ and set $h=\kappa\delta$ with $0<\delta\le \delta_0$.
Assume $C_{m,\delta}$ is $\mathrm{buf}$--admissible at $(a,h)$ in the sense of Definition~\ref{def:shift-admissible-hinge}.
Then there exists $\delta_\ast=\delta_\ast(E,m,a,\kappa,\mathrm{buf})>0$ such that for all $0<\delta\le \delta_\ast$,
\[
\boxed{\ \Phi^\star(m,a,\delta,h)\ \ge\ 2\sqrt{\pi}\ }.
\]
In particular, after shrinking $\delta$ if needed (Remark~\ref{rem:monotone-shrink}), an off--axis quartet forces a uniform positive lower bound for $\Phi^\star$.
\end{lemma}

\begin{proof}
Write $F:=E'/E$.  Near each simple zero $v_0$ of $E$ one has $F(v)=\frac{1}{v-v_0}+H(v)$ with $H$ holomorphic near $v_0$.
Under $\mathrm{buf}$--admissibility, the four shifted traces $v(\theta)\pm(a\pm h)$ avoid all zeros, so $\mathcal D_{a,h}(v(\theta))$ is continuous in $\theta$.

Fix $\delta$ and decompose on the circle:
\[
\mathcal D_{a,h}(v(\theta))=\mathcal D^{\rm sing}_{a,h}(v(\theta))+\mathcal R_{a,h}(v(\theta)),
\]
where $\mathcal D^{\rm sing}_{a,h}$ denotes the contribution of the two top zeros $\rho=\pm a+i m$ to $\mathcal D_{a,h}$ (hence it has the same local pole structure as in Lemma~\ref{lem:geo-c4-toy-force}),
and $\mathcal R_{a,h}$ is continuous on $C_{m,\delta}$ (it collects all remaining analytic terms).

By Lemma~\ref{lem:geo-c4-toy-force} applied to the singular part,
\[
\frac{\delta^2}{h}\,\bigl\|P_2\Im(\mathcal D^{\rm sing}_{a,h}\circ v)\bigr\|_{L^2}=4\sqrt{\pi}.
\]
For the remainder, the projection is bounded by its $L^2$ norm:
\[
\bigl\|P_2\Im(\mathcal R_{a,h}\circ v)\bigr\|_{L^2}\le \bigl\|\Im(\mathcal R_{a,h}\circ v)\bigr\|_{L^2}
\le \sqrt{2\pi}\,\sup_{\theta}|\mathcal R_{a,h}(v(\theta))|.
\]
Since $\mathcal R_{a,h}$ is continuous in a neighborhood of the center as $\delta\to0$ (all singularities are carried by $\mathcal D^{\rm sing}_{a,h}$),
we have $\sup_{\theta}|\mathcal R_{a,h}(v(\theta))|=O_{E,m,a,\kappa,\mathrm{buf}}(1)$ as $\delta\to 0$.
Multiplying by $\delta^2/h=\delta/(\kappa)$ shows the normalized remainder contribution is $O(\delta)$.
Thus for sufficiently small $\delta$,
\[
\Phi^\star
=\frac{\delta^2}{h}\,\bigl\|P_2(\psi^{\rm sing}+\psi^{\rm rem})\bigr\|_{L^2}
\ge
4\sqrt{\pi}-O(\delta)\ \ge\ 2\sqrt{\pi},
\]
as claimed.
\end{proof}

\begin{lemma}[Quartet-induced $L^1$ blow-up on the hinge circle (toy model)]\label{lem:geo-c4-l1-blowup}
In the single-quartet toy model of Lemma \ref{lem:geo-c4-toy-force}, with $v(\theta)=i m+\delta e^{i\theta}$ and $h=\kappa\delta$ ($\kappa\in(0,1)$), the singular contribution
\[
\mathcal D^{\mathrm{sing}}_{a,h}\big(v(\theta)\big)=-\frac{4h}{\delta^2 e^{2i\theta}-h^2}
\]
satisfies the lower bound
\[
\int_0^{2\pi}\left|\mathcal D^{\mathrm{sing}}_{a,h}\big(v(\theta)\big)\right|\,d\theta
\ \ge\ \frac{8\pi}{1+\kappa^2}\,\frac{h}{\delta^2}.
\]
In particular, any UE-input of the form $\int_0^{2\pi}|\mathcal D_{a,h}(v(\theta))|\,d\theta\ll h\,(\log m)^C/a^2$
is incompatible with the presence of an off-axis quartet at that height.
\end{lemma}

\begin{proof}
For $h=\kappa\delta$ one has
\[
\left|\mathcal D^{\mathrm{sing}}_{a,h}\big(v(\theta)\big)\right|
=
\frac{4h}{\left|\delta^2 e^{2i\theta}-h^2\right|}
=
\frac{4h}{\delta^2\,|e^{2i\theta}-\kappa^2|}
\ge
\frac{4h}{\delta^2(1+\kappa^2)},
\]
since $|e^{2i\theta}-\kappa^2|\le |e^{2i\theta}|+|\kappa^2|=1+\kappa^2$.
Integrating over $\theta\in[0,2\pi]$ gives the stated bound.
\end{proof}


\subsubsection{UE reduction via harmonic extraction (boundary $H^1$ control)}

The point of GEO--C4 is that the endpoint is a \emph{single Fourier channel}.  This permits a deterministic UE reduction that does \emph{not} require pointwise control of $\frac{E'}{E}$ on the contour: the $k=2$ Fourier coefficient is bounded by the $L^1$ size of the signal.
Concretely, writing
\[
A_c:=\int_0^{2\pi}\psi(\theta)\cos(2\theta)\,d\theta,\qquad
A_s:=\int_0^{2\pi}\psi(\theta)\sin(2\theta)\,d\theta,
\]
one has $\|P_2\psi\|_{L^2}=\frac{1}{\sqrt{\pi}}\sqrt{A_c^2+A_s^2}$ and
$\sqrt{A_c^2+A_s^2}\le \int_0^{2\pi}|\psi(\theta)|\,d\theta$ since $(\cos(2\theta),\sin(2\theta))$ has unit length.
Thus UE for $\Phi^\star$ reduces to a boundary $H^1$ (i.e.\ $L^1$) control of $\mathcal D_{a,h}$ on the hinge circle.\begin{lemma}[UE reduction from a boundary $H^1$ control]\label{lem:geo-c4-ue-reduction}
Let $v(\theta)=i m+\delta e^{i\theta}$ and $\psi(\theta)=\Im\big(\mathcal D_{a,h}(v(\theta))\big)$.
Then
\[
\|P_2\psi\|_{L^2([0,2\pi])}
=\frac{1}{\sqrt{\pi}}\sqrt{A_c^2+A_s^2}
\le \frac{1}{\sqrt{\pi}}\int_0^{2\pi}|\psi(\theta)|\,d\theta
\le \frac{1}{\sqrt{\pi}}\int_0^{2\pi}\left|\mathcal D_{a,h}(v(\theta))\right|\,d\theta,
\]
and therefore
\[
\boxed{\ \Phi^\star(m,a,\delta,h)\ \le\ \frac{\delta^2}{\sqrt{\pi}\,h}\int_0^{2\pi}\left|\mathcal D_{a,h}(v(\theta))\right|\,d\theta\ }.
\]
\end{lemma}

\begin{proof}
Write $A_c,A_s$ for the $k=2$ Fourier coefficients of $\psi$ as above.  Since $(\cos(2\theta),\sin(2\theta))$ has unit Euclidean norm,
\[
\sqrt{A_c^2+A_s^2}
=
\left\|\int_0^{2\pi}\psi(\theta)\,(\cos(2\theta),\sin(2\theta))\,d\theta\right\|
\le
\int_0^{2\pi}|\psi(\theta)|\,d\theta.
\]
Moreover $|\psi(\theta)|\le |\mathcal D_{a,h}(v(\theta))|$ because $|\Im z|\le |z|$.  The stated bound for $\Phi^\star$ follows by multiplying by $\delta^2/h$.
\end{proof}

\begin{proof}
Let $\widehat\psi(2):=\int_0^{2\pi}\psi(\theta)e^{-2i\theta}\,d\theta$.  Since $\psi$ is $2\pi$--periodic,
two integrations by parts give
\[
\widehat\psi(2)=\frac{1}{(-2i)^2}\int_0^{2\pi}\psi''(\theta)e^{-2i\theta}\,d\theta,
\qquad
|\widehat\psi(2)|\le \frac14\int_0^{2\pi}|\psi''(\theta)|\,d\theta.
\]
The $k=2$ projection satisfies $\|P_2\psi\|_{L^2}\asymp |\widehat\psi(2)|$ (up to absolute constants), so it suffices to bound $\int|\psi''|$.

Write $v(\theta)=i m+\delta e^{i\theta}$ so $|v'(\theta)|=\delta$ and $|v''(\theta)|=\delta$.
By the chain rule,
\[
|\psi''(\theta)|
\ \ll\
\delta^2\cdot\bigl|\partial_v^2\mathcal D_{a,h}(v(\theta))\bigr|
+\delta\cdot\bigl|\partial_v\mathcal D_{a,h}(v(\theta))\bigr|.
\]
Using the assumed bounds and integrating over $\theta$ yields
\[
\int_0^{2\pi}|\psi''(\theta)|\,d\theta
\ \ll\
2\pi\Bigl(\delta^2\cdot h\,A(m,a)\,a^{-4}+\delta\cdot h\,A(m,a)\,a^{-3}\Bigr)
\ \ll\
h\,A(m,a)\,\delta\,a^{-3},
\]
since $\delta\le a$ in the RH regime.
Therefore $|\widehat\psi(2)|\ll h\,A(m,a)\,\delta\,a^{-3}$ and hence $\|P_2\psi\|_{L^2}\ll h\,A(m,a)\,\delta\,a^{-3}$.
Finally,
\[
\Phi^\star=\frac{\delta^2}{h}\|P_2\psi\|_{L^2}\ \ll\ A(m,a)\,\frac{\delta^3}{a^3},
\]
as claimed.
\end{proof}

\subsubsection{The single open statement}

\begin{center}
\fbox{%
\begin{minipage}{0.95\textwidth}
\textbf{UE-INPUT (v43, single active statement).}\label{box:ue-input-v43}

\smallskip
Fix $\kappa\in(0,1)$ and let $E$ be the completed even entire object in the $v$--plane.
For all sufficiently large $m$ and all $a\in(0,1)$, set the nominal scale and coupling
\[
\delta=\eta\,\frac{a}{(\log(m+3))^2},\qquad h:=\kappa\delta,
\]
and (if needed) allow smaller $\delta$ to enforce shift--admissibility / buffering on the hinge circle
$v(\theta)=i m+\delta e^{i\theta}$.

\smallskip
\emph{Goal: a boundary $H^1$ bound for the GEO--C4 second difference.}
Prove that there exist absolute constants $C,C'>0$ such that
\[
\boxed{\ \int_0^{2\pi}\left|\mathcal D_{a,h}\big(v(\theta)\big)\right|\,d\theta
\ \le\ C\,h\,\frac{(\log(m+3))^{C'}}{a^{2}}.\ }
\]
Combined with Lemma \ref{lem:geo-c4-ue-reduction} this yields
$\Phi^\star\ll \eta^2(\log(m+3))^{C'-4}$, so any exponent budget $C'<4$ (or $C'=4$ with $\eta$ chosen small) closes the UE side against the forcing constant.

\end{minipage}}
\end{center}

\subsubsection{Dependency map and NO--GO cross-check}

The active dependency chain is now:
\[
\boxed{
(\pm a\pm i m)\in Z(E)\ \Rightarrow\ \Phi^\star\ge c_0
\quad\text{and}\quad
\text{UE-INPUT}\Rightarrow \Phi^\star=o(1)
\ \Rightarrow\ a=0\ \Rightarrow\ \mathrm{RH}.}
\]

\begin{center}
\begin{tabular}{|p{0.42\textwidth}|p{0.5\textwidth}|}
\hline
\textbf{Archived NO--GO / obstruction (v40--v41)} & \textbf{How GEO--C4 avoids it (v43)}\\
\hline
Centered defect endpoint for $\mathcal L_a$ cancels to $O(\delta/a)$. & GEO--C4 uses the \emph{double difference} $\mathcal D_{a,h}$ and reads a $k=2$ harmonic channel forced by the dipole kernel $-4h/(u^2-h^2)$.\\
\hline
$\delta$--inert resonance for pointwise/sidewise shift endpoints (near-resonant second quartet). & We allow monotone admissibility shrink in $\delta$ and use an orthogonal projection endpoint; the forcing survives shrink (Lemma~\ref{lem:geo-c4-force-stable}).\\
\hline
Aligned-box micro-coupling (NG-$\Delta a$-A) suppresses forcing by $\delta h/a^2$. & GEO--C4 is hinge-centered: the singularities of $\mathcal D_{a,h}$ occur at $v=i m\pm h$ inside the witness disk, so there is no $a^{-2}$ suppression.\\
\hline
Pointwise UE ceiling: $\sup|E'/E|$ on a boundary cannot beat forcing. & Harmonic extraction allows integration by parts: $k=2$ projection converts derivative bounds into extra $\delta$ powers (Lemma~\ref{lem:geo-c4-ue-reduction}).\\
\hline
\end{tabular}
\end{center}





\begin{lemma}[Endpoint-only NO--GO: $\theta=0$ per pole forbids any $p>0$ UE gain]
\label{lem:phase-UE-theta0-nogo}
Fix $\kappa\in(0,1/10)$. Let $B=B(\alpha,m,\delta)$ be an aligned box and assume $\kappa$--admissibility so that
$\widetilde D_B(W)$ is defined (Definition~\ref{def:Db-tilde-phase}).
Let $E$ be holomorphic on a neighborhood of $\overline B$ with outer factorization $E=G_{\rm out}\,W$ on $B$.

Assume $\Phi_B$ is a boundary functional acting on the trace of $E'/E$ and that
there exist constants $C_{\rm loc}=C_{\rm loc}(\kappa)$ and $u\ge 0$ such that,
for every $\rho\in B_{\kappa/2}$ and the test function $E_\rho(v):=v-\rho$, one has
the per-pole bound
\[
\Phi_B\!\left(\frac{E_\rho'}{E_\rho}\right)
=\Phi_B\!\left(\frac1{v-\rho}\right)
\le C_{\rm loc}\,\kappa^{-u},
\]
uniformly in $\delta$ (this is the strong form of ``$\theta=0$ per pole'').

Then there do not exist constants $C_{\rm up}>0$ and $p>0$ (independent of $\delta$)
such that the phase-class UE inequality
\[
\widetilde D_B(W) \;\le\; C_{\rm up}\,\delta^{p}\,\Phi_B\!\left(\frac{E'}{E}\right)
\]
holds for all such boxes $B$ and all such holomorphic $E$.
In fact, for $E=E_\rho(v)=v-\rho$ with $\rho\in B_{\kappa/2}$, the inequality forces
\[
\frac{\pi}{2} \;\le\; C_{\rm up}\,C_{\rm loc}\,\kappa^{-u}\,\delta^{p},
\]
which fails for sufficiently small $\delta$.
\end{lemma}

\begin{proof}
Fix $\rho\in B_{\kappa/2}$ and take $E(v)=E_\rho(v)=v-\rho$.
Then $E$ has a zero in $B_{\kappa/2}^\circ$, hence its quotient $W=E/G_{\rm out}$ also has a zero there
(since $G_{\rm out}$ is holomorphic and zero-free on $B^\circ$).
By Lemma~\ref{lem:phase-forcing-argprinciple} this implies $\widetilde D_B(W)\ge \pi/2$.
On the other hand $E'/E=1/(v-\rho)$, so by hypothesis
$\Phi_B(E'/E)\le C_{\rm loc}\kappa^{-u}$ uniformly in $\delta$.
Substituting into the claimed UE bound gives
$\pi/2 \le C_{\rm up}C_{\rm loc}\kappa^{-u}\delta^{p}$, contradicting $p>0$ as $\delta\to 0$.
\end{proof}

\begin{remark}[Consequence: endpoint-only $\theta=0$ cannot yield any $p>0$ gain]
Any attempt to close the S5$'$ envelope obligation by choosing an endpoint class $\Phi_B$ that is $\delta$--inert on each
local Cauchy kernel $(v-\rho)^{-1}$ (``$\theta=0$ per pole'') cannot produce a $\delta^p$ UE gain with
$p>0$ via a purely local analytic argument: the test input $E(v)=v-\rho$ contradicts such a bound
(Lemma~\ref{lem:phase-UE-theta0-nogo}). Therefore any successful phase-class UE inequality with
$p\ge 1/2$ must incorporate additional structure that defeats the one-pole model (e.g.\ forcing redesign
or pair-isolation/cancellation in the local factor).
\end{remark}

\begin{lemma}[LOCAL isolation needed to beat the one-pole obstruction]
\label{lem:local-isolation-needed}
Fix $\kappa\in(0,1/10)$ and let $\Phi_B$ be the endpoint class targeted in S5$'$.
To obtain any UE gain $p>0$ with a local exponent $\theta<p$ in the S5$'$ budget theorem,
it is necessary to prove a structural statement of the following form:

Whenever $B=B(\alpha,m,\delta)$ is $\kappa$-admissible at the nominal scale
$\delta\le \delta_0(m,\alpha)$ and $Z_{\rm loc}$ is the local factor of $E$ on $B$,
there exists a factorization
\[
Z_{\rm loc} \;=\; Z_{\rm forced}\cdot Z_{\rm rest}
\]
such that (i) $Z_{\rm forced}$ contains only $O(1)$ zeros (the ``forced pair''), and (ii)
\emph{in the chosen endpoint class} one has a $\delta$-small bound
\[
\Phi_B\!\left(\frac{Z_{\rm rest}'}{Z_{\rm rest}}\right)
\;\le\;
C\,\kappa^{-u}\,(\log m)^{q_{\rm eff}}\,\delta^{-(\theta_{\rm eff})}
\qquad\text{with}\qquad \theta_{\rm eff}<p
\]
(and ideally $\theta_{\rm eff}=0$ with $q_{\rm eff}=0$ or with an extra $\delta$ factor).
\end{lemma}




\begin{remark}[S5 acceptance criterion (budget calculus; no drift)]
\label{rem:S5-accept}
Any proposed S5 redesign must specify a boundary functional $\Phi_B$ (shape--invariant; $\delta$--normalized)
and prove two explicit inequalities uniformly for all $m\ge 10$, all $\alpha\in(0,1]$, and all
$\kappa$--admissible $0<\delta\le \delta_0(m,\alpha)=\eta\alpha/(\log m)^2$:

\begin{enumerate}[leftmargin=1.5em]
\item \textbf{(S5--UE)} a forceable upper-envelope bound
\[
D_B(W)\le C_{\rm up}\,\delta^{p}\,\Phi_B(E'/E)
\]
with an explicit exponent $p>0$ and $\delta$--uniform constant $C_{\rm up}$;

\item \textbf{(S5--LOC)} a local/collar bound in the same endpoint class
\[
\Phi_B(Z'_{\rm loc}/Z_{\rm loc})\le C_{\rm loc}\,\delta^{-\theta}\,G(N_{\rm loc}(m),\kappa)
\]
with explicit $\theta\ge 0$ and an explicit growth model for $G$ (e.g.\ $G(n,\kappa)\ll \kappa^{-u}n^q$).
\end{enumerate}

The redesign is budget--viable for uniform $\eta$--shrinking closure under $\delta_0$
only if the S5 Budget Theorem yields $2(p-\theta)\ge q$ (and $p-\theta>0$ for shrinkability).
If $p-\theta<0$, the standard $\kappa$--admissible shrink policy is unsafe (shrinking $\delta$ can
increase the envelope term) and must be redesigned.

Finally, the forcing chain remains phrased in terms of $D_B(W)$; therefore S5 must include either
$\Phi_B\ge D_B(W)$ on all admissible boxes or a new forcing lemma that lower-bounds $\Phi_B$
directly (Remark~\ref{rem:s5-forceability-gate}).
\end{remark}


\begin{theorem}[S5 Budget Theorem (general endpoint functional)]
\label{thm:S5-budget}
Fix $\eta\in(0,1]$ and $\kappa\in(0,1/10)$ and define the nominal scale $\delta_0(m,\alpha)=\eta\alpha/(\log m)^2$.
Let $\Phi_B$ be a boundary functional and assume that for every $m\ge 10$, $\alpha\in(0,1]$, and every
$\kappa$--admissible $0<\delta\le \delta_0(m,\alpha)$ one has:
\begin{enumerate}[leftmargin=1.5em]
\item[(i)] \textbf{(S5--UE)} $D_B(W)\le C_{\rm up}\,\delta^{p}\,\Phi_B(E'/E)$ for some $p>0$ and $\delta$--uniform constant $C_{\rm up}$;
\item[(ii)] \textbf{(S5--SPLIT)} $\Phi_B(E'/E)\le \mathrm{Res}(m)+\Phi_B(Z'_{\rm loc}/Z_{\rm loc})$;
\item[(iii)] \textbf{(S5--LOC)} $\Phi_B(Z'_{\rm loc}/Z_{\rm loc})\le C_{\rm loc}\,\delta^{-\theta}\,G(N_{\rm loc}(m),\kappa)$ for some $\theta\ge 0$ and $\delta$--uniform $C_{\rm loc}$.
\end{enumerate}
Assume moreover that $N_{\rm loc}(m)\le A_N\log m+B_N$ and $\mathrm{Res}(m)\le A_L(\log m)^{r_L}+B_L$ for absolute constants,
and that for some $q,u\ge 0$ one has the growth model
\[
G(n,\kappa)\le C_G\,\kappa^{-u}\,n^q\qquad (n\ge 1),
\]
with $C_G$ independent of $(m,\alpha,\delta)$.

Then at the nominal choice $\delta=\delta_0(m,\alpha)$,
\begin{equation}
\label{eq:S5-budget}
D_B(W)\ \le\
C_{\rm up}\Bigl(\delta_0^{p}\,\mathrm{Res}(m)\ +\ C_{\rm loc}\,\delta_0^{p-\theta}\,G(N_{\rm loc}(m),\kappa)\Bigr).
\end{equation}
Furthermore:
\begin{enumerate}[leftmargin=1.5em]
\item \textbf{(Uniformity in $m$)} The local contribution in \eqref{eq:S5-budget} is uniformly bounded in $m\ge 10$ only if
\begin{equation}
\label{eq:S5-budget-condition}
2(p-\theta)\ \ge\ q.
\end{equation}
\item \textbf{($\eta$--shrinkability)} If \eqref{eq:S5-budget-condition} holds and $p-\theta>0$, then
\[
\sup_{m\ge 10}\ \delta_0(m,1)^{p-\theta}\,G(N_{\rm loc}(m),\kappa)\ =\ O\big(\eta^{p-\theta}\big),
\]
so the local penalty can be made arbitrarily small by choosing $\eta$ sufficiently small.
\item \textbf{($\delta$--shrink monotonicity)} If $p\ge 0$ and $p-\theta\ge 0$, then the right-hand side of \eqref{eq:S5-budget}
is nondecreasing in $\delta$ (for fixed $m,\alpha$); hence replacing $\delta_0$ by a smaller $\kappa$--admissible $\delta\le\delta_0$
can only improve the inequality. If $p-\theta<0$, $\kappa$--shrinking can \emph{worsen} the envelope term.
\end{enumerate}
\end{theorem}

\begin{proof}
Combine (S5--UE) with (S5--SPLIT) and (S5--LOC) to obtain
\[
D_B(W)\le C_{\rm up}\,\delta^{p}\,\mathrm{Res}(m)+C_{\rm up}\,C_{\rm loc}\,\delta^{p-\theta}\,G(N_{\rm loc}(m),\kappa).
\]
Set $\delta=\delta_0(m,\alpha)$ to obtain \eqref{eq:S5-budget}.

For the local contribution at $\alpha=1$ use $\delta_0=\eta/(\log m)^2$, the growth model $G(n,\kappa)\le C_G\kappa^{-u}n^q$,
and $N_{\rm loc}(m)\ll\log m$ to get
\[
\delta_0^{p-\theta}\,G(N_{\rm loc}(m),\kappa)
\ \ll\
\kappa^{-u}\,\eta^{p-\theta}\,(\log m)^{-2(p-\theta)}\,(\log m)^{q}
=\kappa^{-u}\,\eta^{p-\theta}\,(\log m)^{q-2(p-\theta)}.
\]
This is uniformly bounded in $m$ only if $q-2(p-\theta)\le 0$, i.e.\ \eqref{eq:S5-budget-condition}.
If additionally $p-\theta>0$, the factor $\eta^{p-\theta}$ yields $\eta$--shrinkability.

Finally, the monotonicity claim follows because $\delta\mapsto \delta^{p}$ and $\delta\mapsto \delta^{p-\theta}$ are
nondecreasing on $(0,\infty)$ exactly when $p\ge 0$ and $p-\theta\ge 0$.
\end{proof}

% ============================================================
% v39: S5' closure criterion (budget spine) + acceptance gate
% ============================================================

\begin{theorem}[S5$'$ closure from a forceable phase endpoint]\label{thm:S5prime-closure}
Fix $\kappa\in(0,1/10)$ and $\eta\in(0,1)$ and define $\delta_0(m,\alpha)=\eta\alpha/(\log m)^2$.
Let $\widetilde D_B$ be a boundary phase endpoint functional assigned to each $\kappa$--admissible
aligned box $B=B(\pm a,m,\delta)$ and its boundary quotient $W$.
Assume:
\begin{enumerate}[leftmargin=1.5em]
  \item[(S5$'$--FORCE)] Under an off-axis quartet at height $m$ with displacement $a>0$,
  there exists an aligned $\kappa$--admissible box $B$ (with $\alpha\approx a$) such that
  $\widetilde D_B(W)\ge c_{\rm force}-\delta\,\Xi(m)$ with $c_{\rm force}>0$ absolute and
  $\Xi(m)\ge 0$ explicit.
  \item[(S5$'$--UE+SPLIT)] For every $\kappa$--admissible aligned box,
  \[
    \widetilde D_B(W)\le C_{\rm up}\,\delta^p\Big(\mathrm{Res}(m)+C_{\rm loc}\,\delta^{-\theta}\,G(N_{\rm loc}(m),\kappa)\Big),
  \]
  where $p>0$, $\theta\ge 0$, and $C_{\rm up},C_{\rm loc}$ are $\delta$--uniform, and
  $G(n,\kappa)\le C_G\,\kappa^{-u}n^q$ for fixed $u,q\ge 0$.
\end{enumerate}
Suppose additionally that $2p\ge 1$, $2(p-\theta)\ge q$, and $p-\theta>0$.
Then there exists $\eta_\star\in(0,1)$ (depending on the displayed constants and $\kappa$) such that
for every $\eta\in(0,\eta_\star]$ the S5$'$ tail inequality holds at $\delta=\delta_0(m,\alpha)$
for all $m\ge 10$ and all $\alpha\in(0,1]$, and hence no off-axis quartet exists at any height $m\ge 10$.
Combined with any finite-height front-end, this implies RH.
\end{theorem}

\begin{remark}[S5$'$ acceptance gate for phase endpoints (no drift)]\label{rem:S5prime-gate}
Any proposed S5$'$ endpoint built from boundary phase data (e.g.\ $\Delta\arg$ or an integral of
$\Im(\log\text{-derivative})$) must declare its exponent budget data $(p,\theta,q)$ in the
schematic bound
\[
  \widetilde D_B(W)\le C_{\rm up}\,\delta^p\Big(\mathrm{Res}(m)+C_{\rm loc}\,\delta^{-\theta}\,G(N_{\rm loc}(m),\kappa)\Big),
\]
and must satisfy the uniformity/shrink conditions of Theorem~\ref{thm:S5prime-closure}:
$2p\ge 1$, $2(p-\theta)\ge q$, and $p-\theta>0$.
Pure $\Delta\arg$ endpoints have $p=0$ and are rejected.
Any phase endpoint whose proof reduces to an absolute $L^r(\partial B)$ estimate for $E'/E$
is also rejected by Lemma~\ref{lem:S5_Lp_collapse} and Proposition~\ref{prop:S5_Lp_nogo}.
\end{remark}




At fixed $(m,\alpha)$ the tail inequality \eqref{eq:tail-ineq} is a strict forcing--vs--envelope condition.
In v39 (inherited from v36) the combination of Theorem~\ref{thm:exponent-budget}, Lemma~\ref{lem:UE-scaling-nogo}, and Lemma~\ref{lem:force-constant-limited}
formally rules out the former ``$\eta$--absorption'' closure route based on the pointwise/sup endpoint
$\sup_{\partial B}|E'/E|$ together with the pointwise collar bound.

\medskip
\noindent\textbf{What must change.}
The forcing chain produces a lower bound for the \emph{dial deviation}
\[
D_B(W)\ :=\ \sum_{\pm}\bigl|W(v_\pm)-e^{i\varphi_0^\pm}\bigr|
\]
appearing in Lemma~\ref{lem:upper-envelope}.
In the current architecture this deviation is upper-bounded by a pointwise endpoint
$\delta\,\sup_{\partial B}|E'/E|$, which (via the collar) introduces the sharp $\delta^{-1}$ blow--up.
To obtain a tail closure mechanism one must redesign the envelope endpoint and/or the local interface so that the exponent budget
$p-\theta\ge \tfrac12$ is met \emph{uniformly in $m$}.

\begin{remark}[Forcing compatibility for redesigned endpoints]
\label{rem:forceability}
The existing forcing chain lower-bounds $D_B(W)$ (via the pair-factor phase rotation) by a fixed constant $c$ up to $\delta$--small corrections.
If one proposes a redesigned envelope endpoint $\Phi_B$ (non-pointwise, e.g.\ an $L^2$ or energy functional),
then the current forcing lower bound is useful only if it implies a corresponding lower bound for $\Phi_B$.
A sufficient (and simplest) compatibility condition is:
\[
\Phi_B\ \ge\ D_B(W)\qquad\text{for all admissible boxes and quotients }W,
\]
so that the forcing lower bound propagates unchanged.
If this domination fails, then a \emph{new forcing lemma} must be proved that lower-bounds $\Phi_B$ directly.
\end{remark}




\begin{lemma}[Forceability transfer by domination]
\label{lem:forceability-domination}
Let $B$ be a $\kappa$--admissible aligned box and $W$ the associated boundary quotient.
Suppose a boundary endpoint functional $\Phi_B$ satisfies
\[
\Phi_B \ge D_B(W)
\quad\text{for all admissible }(B,W).
\]
Then the existing single--box forcing lower bound for $D_B(W)$ implies the same forcing lower bound
for $\Phi_B$ with no change in the forcing constants.
\end{lemma}


\begin{remark}[Forceability gate for S5 endpoints (NO--GO unless met)]
\label{rem:s5-forceability-gate}
The current forcing architecture (Section~\ref{sec:forcing}) forces only the dial deviation $D_B(W)$
by an $O(1)$ constant up to $\delta$--small deductions (Lemma~\ref{lem:force-constant-limited}).
Consequently, any S5 redesign that replaces $D_B(W)$ by a different endpoint $\widetilde D_B$ (or $\Phi_B$)
is \emph{invalid} unless it proves either:
\begin{enumerate}[leftmargin=1.5em]
\item[(i)] $\widetilde D_B \ge D_B(W)$ for all admissible boxes/quotients (domination transfer), or
\item[(ii)] a new forcing lemma that lower--bounds $\widetilde D_B$ directly under an off--axis quartet.
\end{enumerate}
Without (i) or (ii), the forcing half of the tail inequality becomes logically disconnected from the envelope half.
\end{remark}

% ============================================================
% v39: S5' phase endpoint toolkit + buffered phase forcing
% Inserted after Remark~\ref{rem:s5-forceability-gate}.
% ============================================================

\subsection{S5$'$ phase endpoints: winding / argument-increment toolkit}\label{subsec:S5prime-phase-toolkit}

\begin{definition}[Phase increment on a boundary arc]\label{def:phase_increment}
Let $\Gamma\subset\mathbb{C}$ be a piecewise $C^1$ oriented curve and let $f$ be holomorphic
on an open neighborhood of $\Gamma$ with $f(v)\neq 0$ for all $v\in\Gamma$.
Define the phase increment of $f$ along $\Gamma$ by
\[
\Delta_{\Gamma}\arg f \ :=\ \Im\int_{\Gamma}\frac{f'(v)}{f(v)}\,dv.
\]
(Equivalently, $\Delta_{\Gamma}\arg f$ is the total change of a continuous branch of $\arg f$ along $\Gamma$.)
\end{definition}

\begin{lemma}[Phase increment identity and vertical specialization]\label{lem:phase_increment_identity}
Under the hypotheses of Definition~\ref{def:phase_increment}, the phase increment is additive under concatenation of curves and satisfies:
\begin{enumerate}[leftmargin=1.5em]
\item If $\Gamma=\Gamma_1\cup\Gamma_2$ (oriented concatenation), then $\Delta_{\Gamma}\arg f=\Delta_{\Gamma_1}\arg f+\Delta_{\Gamma_2}\arg f$.
\item If $\Gamma$ is the vertical segment $I_+:=\{\alpha+i y:\ |y-m|\le \delta\}$ oriented upward, then
\[
\Delta_{I_+}\arg f \ =\ \Im\int_{m-\delta}^{m+\delta}\frac{f'(\alpha+i y)}{f(\alpha+i y)}\,i\,dy
\ =\ \int_{m-\delta}^{m+\delta}\Re\!\left(\frac{f'(\alpha+i y)}{f(\alpha+i y)}\right)\,dy.
\]
\end{enumerate}
\end{lemma}

\begin{remark}[Parentheses hygiene for phase endpoints]\label{rem:phase_parentheses_hygiene}
For non-horizontal arcs, one must distinguish
\[
\Im\int_{\Gamma}\frac{f'}{f}\,dv
\qquad\text{from}\qquad
\int_{\Gamma}\Im\!\left(\frac{f'}{f}\right)\,dv.
\]
Only the former is a phase increment. This distinction is essential on vertical segments where $dv=i\,dy$.
\end{remark}

\begin{definition}[Shifted near-vertical segment]\label{def:Iplus_lambda}
Let $B=B(\alpha,m,\delta)$ be an aligned box and let $\lambda\in(0,1)$.
Define the shifted segment
\[
I_{+,\lambda}:=\{\alpha+\lambda\delta+i y:\ |y-m|\le \delta\},
\]
oriented upward. (\emph{This lies strictly inside $B$. It is separated from the unshifted vertical line
$I_+=\{\alpha+iy:|y-m|\le\delta\}$ by horizontal distance $\lambda\delta$, and its distance to $\partial B$
 is at least $(1-\lambda)\delta$.})
\end{definition}

\begin{lemma}[Phase split on $I_{+,\lambda}$]\label{lem:phase_split_Iplus_lambda}
Let $B=B(\alpha,m,\delta)$ be $\kappa$--admissible and aligned, and let $I_{+,\lambda}$ be as in Definition~\ref{def:Iplus_lambda}.
Assume $E$, $Z_{\rm loc}$ and $F:=E/Z_{\rm loc}$ are holomorphic and nonvanishing on an open neighborhood of $I_{+,\lambda}$.
Then
\[
\Delta_{I_{+,\lambda}}\arg E \ =\ \Delta_{I_{+,\lambda}}\arg F\ +\ \Delta_{I_{+,\lambda}}\arg Z_{\rm loc}.
\]
Moreover,
\[
\bigl|\Delta_{I_{+,\lambda}}\arg F\bigr|
\ \le\ 2\delta\ \sup_{v\in I_{+,\lambda}}\left|\frac{F'(v)}{F(v)}\right|
\ \le\ 2\delta\ \sup_{v\in\partial B}\left|\frac{F'(v)}{F(v)}\right|.
\]
\end{lemma}

\begin{corollary}[Residual phase budget ($\delta$--uniform)]\label{cor:residual_phase_budget}
Assume the residual envelope bound of Lemma~\ref{lem:residual-envelope}, i.e.
$\sup_{\partial B}|F'/F|\le C_1\log m+C_2$ on every $\kappa$--admissible aligned box.
Then, for every $\lambda\in(0,1)$,
\[
\bigl|\Delta_{I_{+,\lambda}}\arg F\bigr|\ \le\ 2\delta\,(C_1\log m+C_2).
\]
\end{corollary}

\begin{lemma}[Local phase is $\delta$--inert on line segments (per-zero contribution is $O(1)$)]
\label{lem:local_phase_delta_inert}
Let $S\subset\mathbb C$ be any oriented line segment and let $\rho\notin S$.
Choose a continuous branch of $\arg(v-\rho)$ along $S$.
Then
\[
\left|\Im\int_{S}\frac{dv}{v-\rho}\right|
=\left|\arg(v_1-\rho)-\arg(v_0-\rho)\right|
\le \pi,
\]
where $v_0,v_1$ are the endpoints of $S$.
Consequently, writing $Z_{\rm loc}(v)=\prod_{\rho\in Z_{\rm loc}(m)}(v-\rho)^{m_\rho}$,
for any segment $S$ avoiding $Z_{\rm loc}(m)$ one has
\[
\left|\Im\int_{S}\frac{Z'_{\rm loc}(v)}{Z_{\rm loc}(v)}\,dv\right|
=\left|\Delta_{S}\arg Z_{\rm loc}\right|
\le \pi\,N_{\rm loc}(m).
\]
\end{lemma}

\begin{corollary}[Prototype phase upper bound (residual + local)]\label{cor:prototype_phase_upper}
Under the hypotheses of Lemma~\ref{lem:phase_split_Iplus_lambda} and Corollary~\ref{cor:residual_phase_budget},
\[
\bigl|\Delta_{I_{+,\lambda}}\arg E\bigr|
\le 2\delta\,(C_1\log m+C_2)\ +\ \bigl|\Delta_{I_{+,\lambda}}\arg Z_{\rm loc}\bigr|.
\]
In particular, the residual contribution is $O(\delta\log m)$ while the local contribution is $\delta$--inert in the phase class.
\end{corollary}

% ------------------------------------------------------------
% Buffered boundary phase endpoint + forcing lemma (\pi/2)
% ------------------------------------------------------------

\begin{definition}[Buffered boundary phase endpoint]\label{def:Db-tilde-phase}
Let $B=B(\alpha,m,\delta)$ be an aligned box and assume $\kappa$--admissibility:
$\dist(\partial B, Z(E))\ge \kappa\delta$.
Let $G_{\rm out}$ be the Dirichlet outer factor on $B^\circ$ and $W:=E/G_{\rm out}$ the inner quotient.
Define the buffered inner rectangle
\[
B_{\kappa/2}:=\{v\in B:\dist(v,\partial B)\ge \tfrac{\kappa\delta}{2}\},
\]
and write its oriented boundary as $\partial B_{\kappa/2}=\bigcup_{j=1}^4 S_j$ (counterclockwise).
Define the sidewise phase increment
\[
\Delta_{S_j}\arg W \ :=\ \Im\int_{S_j}\frac{W'(v)}{W(v)}\,dv,
\]
and the phase endpoint
\[
\widetilde D_B(W):=\max_{1\le j\le 4}\Bigl|\Delta_{S_j}\arg W\Bigr|.
\]
\end{definition}

\begin{lemma}[Collar nonvanishing for buffered phase endpoints]
\label{lem:phase_collar_nonvanishing}
Let $B=B(\alpha,m,\delta)$ be $\kappa$--admissible:
$\dist(\partial B,\mathcal Z(E))\ge \kappa\delta$.
Let $B_{\kappa/2}$ be the buffered inner rectangle from Definition~\ref{def:Db-tilde-phase}.
Then
\[
\dist(\partial B_{\kappa/2},\mathcal Z(E))\ \ge\ \frac{\kappa\delta}{2}.
\]
In particular, if $G_{\rm out}$ is the Dirichlet outer factor on $B^\circ$ and $W=E/G_{\rm out}$,
then both $G_{\rm out}$ and $W$ are holomorphic and nonvanishing on an open neighborhood of $\partial B_{\kappa/2}$,
so the phase increments $\Delta_{S_j}\arg W$ are well-defined (no branch crossing).
\end{lemma}

\begin{corollary}[Local term on the buffered boundary phase endpoint class]
\label{cor:local_phase_on_buffered_boundary}
Assume the hypotheses of Definition~\ref{def:Db-tilde-phase} and write $\partial B_{\kappa/2}=\bigcup_{j=1}^4 S_j$.
Then the local factor satisfies
\[
\max_{1\le j\le 4}\left|\Im\int_{S_j}\frac{Z'_{\rm loc}(v)}{Z_{\rm loc}(v)}\,dv\right|
\le \pi\,N_{\rm loc}(m).
\]
Equivalently,
\[
\max_{1\le j\le 4}\left|\Delta_{S_j}\arg Z_{\rm loc}\right|
\le \pi\,N_{\rm loc}(m).
\]
\end{corollary}

\begin{lemma}[Refined per-zero phase bound by horizontal separation]\label{lem:phase_kernel_refined}
Let $S\subset\mathbb C$ be a line segment of length $|S|$ and let $\rho\notin S$.
Write $d:=\dist(\rho,S)$.
Then
\[
\left|\Im\int_{S}\frac{dv}{v-\rho}\right|
\le
\min\left\{\pi,\ \frac{|S|}{d}\right\}.
\]
\end{lemma}



\begin{lemma}[Phase forcing from an interior zero]\label{lem:phase-forcing-argprinciple}
Assume the setup of Definition~\ref{def:Db-tilde-phase}. If $W$ has at least one zero in
$B_{\kappa/2}^\circ$ (equivalently $E$ has at least one zero there), then
\[
\widetilde D_B(W)\ge \frac{\pi}{2}.
\]
\end{lemma}

\begin{proof}
Since $W$ is holomorphic and nonvanishing on a neighborhood of $\partial B_{\kappa/2}$,
the argument principle gives
\[
\oint_{\partial B_{\kappa/2}} \frac{W'(v)}{W(v)}\,dv = 2\pi i\,N,
\]
where $N\ge 1$ is the number of zeros of $W$ in $B_{\kappa/2}^\circ$, counted with multiplicity.
Taking imaginary parts and decomposing $\partial B_{\kappa/2}$ into four sides yields
\[
\sum_{j=1}^4 \Delta_{S_j}\arg W = 2\pi N.
\]
Hence
\[
\widetilde D_B(W)\ \ge\ \frac{1}{4}\left|\sum_{j=1}^4 \Delta_{S_j}\arg W\right|
\ =\ \frac{\pi N}{2}\ \ge\ \frac{\pi}{2}.
\]
\end{proof}

\begin{corollary}[Forcing hypothesis is automatic for the buffered phase endpoint]
\label{cor:S5prime-force-automatic}
Let $\widetilde D_B$ be the buffered boundary phase endpoint of Definition~\ref{def:Db-tilde-phase}.
Then whenever $W$ has a zero in $B_{\kappa/2}^\circ$ one has $\widetilde D_B(W)\ge \pi/2$.
In particular, in Theorem~\ref{thm:S5prime-closure} the forcing condition {\rm(S5$'$--FORCE)}
may be taken with $c_{\rm force}=\pi/2$ and $\Xi(m)\equiv 0$ whenever the contradiction endpoint
is $\widetilde D_B$.
\end{corollary}

\begin{proof}
This is exactly Lemma~\ref{lem:phase-forcing-argprinciple}.
\end{proof}

\begin{remark}[Forceability gate for phase endpoints]\label{rem:forceability-phase-gate}
The single-box forcing chain in this manuscript supplies a lower bound only for a \emph{forced endpoint}.
For the buffered phase endpoint $\widetilde D_B$ this lower bound is provided by Lemma~\ref{lem:phase-forcing-argprinciple}
(and recorded as a hypothesis-discharge in Corollary~\ref{cor:S5prime-force-automatic}).
Consequently, any proposed S5$'$ contradiction endpoint $\Phi_B$ is admissible only if either:
\begin{enumerate}[leftmargin=1.5em]
\item $\Phi_B(W)\ge \widetilde D_B(W)$ on every $\kappa$--admissible aligned box (forcing transfers), or
\item a new forcing lemma is proved that lower-bounds $\Phi_B(W)$ directly under an interior zero/off-axis quartet.
\end{enumerate}
Without such a link, forcing and envelope are logically disconnected.
\end{remark}




\subsection{Baseline NO--GO results for naive non-pointwise endpoints}
\label{subsec:S5-nogo-baseline}

The S5 goal is to replace the pointwise/sup endpoint in Lemma~\ref{lem:upper-envelope}
by a non--pointwise functional that still controls the same dial deviation $D_B(W)$ appearing in the forcing chain.
The next two results prevent drift into two large endpoint classes that cannot work under the present $D_B(W)$ target
and the v36 local split/collar interface (unchanged from v35).


\begin{lemma}[Absolute $L^r$ endpoint scaling collapse]
\label{lem:S5_Lp_collapse}
Let $B=B(\pm a,m,\delta)$ be an aligned box and let $G_{\rm out}$ and $W=E/G_{\rm out}$ be as in
Lemma~\ref{lem:upper-envelope}. Assume boundary contact so that $W$ has unimodular boundary values a.e.
Fix $r\in[1,\infty]$ and write $L^r(\partial B)$ for $L^r(\partial B,ds)$.
Then there exists a shape-only constant $C_r>0$ (depending only on the normalized square $Q=[-1,1]^2$)
such that for each sign $\pm$,
\begin{equation}
\label{eq:S5-Lr-UE}
\bigl|W(v_\pm)-e^{i\varphi_0^\pm}\bigr|
\ \le\ C_r\,\delta^{\,1-1/r}\,
\Bigl\|\frac{E'}{E}\Bigr\|_{L^r(\partial B)}.
\end{equation}
In particular, any upper-envelope mechanism whose endpoint is an \emph{absolute} $L^r(\partial B)$ norm of $E'/E$
cannot have a $\delta$--prefactor exponent exceeding $p(r)=1-1/r$ within this endpoint class.
\end{lemma}

\begin{proof}
Repeat the proof of Lemma~\ref{lem:upper-envelope} with $L^2$ replaced by $L^r$ throughout.
Evaluation from the boundary gives $|W(v_\pm)-c|\le \|P_B(v_\pm,\cdot)\|_{L^q}\,\|W-c\|_{L^r}$ for $1/r+1/q=1$,
and under affine rescaling $\|P_B\|_{L^q}\asymp \delta^{-1/r}$.
Boundary Poincar\'e in $L^r$ yields $\|W-c\|_{L^r}\le C_r'\,\delta\,\|\partial_s W\|_{L^r}$ with a shape-only constant $C_r'$,
and outer factor control bounds $\|\partial_s W\|_{L^r}$ by a shape-only constant times $\|E'/E\|_{L^r}$.
Choosing $c=e^{i\varphi_0^\pm}$ gives \eqref{eq:S5-Lr-UE}, with overall factor $\delta^{-1/r}\cdot \delta=\delta^{1-1/r}$.
\end{proof}


\begin{proposition}[NO--GO: absolute $L^r$ log-derivative endpoints cannot clear the UE--Gate]
\label{prop:S5_Lp_nogo}
Assume in addition that $B$ is $\kappa$--admissible and hence the pointwise collar bound holds:
$\sup_{\partial B}|Z'_{\rm loc}/Z_{\rm loc}|\le N_{\rm loc}(m)/(\kappa\delta)$ (Lemma~\ref{lem:Zloc-logder-collar}).
Then for every $r\in[1,\infty]$,
\[
\delta^{\,1-1/r}\left\|\frac{Z'_{\rm loc}}{Z_{\rm loc}}\right\|_{L^r(\partial B)}
\ \le\ 8^{1/r}\,\frac{N_{\rm loc}(m)}{\kappa},
\]
independent of $\delta$.
In particular, under the nominal scale $\delta_0(m,\alpha)=\eta\alpha/(\log m)^2$ and the unconditional majorant
$N_{\rm loc}(m)\ll\log m$, uniform $\eta$--shrinking cannot suppress the local term within any envelope mechanism
whose endpoint is an absolute $L^r(\partial B)$ norm of $E'/E$.
\end{proposition}

\begin{proof}
Use $|\partial B|=8\delta$ and $\|f\|_{L^r}\le |\partial B|^{1/r}\|f\|_{L^\infty}$ to get
\[
\Bigl\|\frac{Z'_{\rm loc}}{Z_{\rm loc}}\Bigr\|_{L^r(\partial B)}
\le (8\delta)^{1/r}\cdot \frac{N_{\rm loc}(m)}{\kappa\delta}
=8^{1/r}\,\frac{N_{\rm loc}(m)}{\kappa\,\delta^{\,1-1/r}}.
\]
Multiply by $\delta^{\,1-1/r}$.
\end{proof}


\begin{remark}[Implication for S5 endpoint design]
\label{rem:S5_endpoint_implication}
Lemmas~\ref{lem:S5_Lp_collapse}--\ref{prop:S5_Lp_nogo} rule out the entire family of S5 proposals that attempt
to replace $\sup_{\partial B}|E'/E|$ by an \emph{absolute} $L^r(\partial B)$ norm of $E'/E$ while keeping the same
$\kappa$--collar local control. Any viable S5 redesign must instead (i) exploit cancellation (argument-principle style
\emph{signed} endpoints) and/or (ii) move to a less singular boundary object (e.g.\ endpoints built from $\log|E|$ / BMO-type control).
\end{remark}


\begin{lemma}[NO--GO: local-kernel projection endpoints cannot control $D_B(W)$ without a new forcing link]
\label{lem:S5-projection-nogo}
Fix an aligned box $B$ and consider an endpoint functional of the form
\[
\Phi_B(E)\ :=\ \|(I-\Pi_B)(E'/E)\|_{X(\partial B)}
\]
for some normed boundary space $X(\partial B)$ and a bounded projection $\Pi_B$ satisfying
$\Pi_B(Z'_{\rm loc}/Z_{\rm loc})=Z'_{\rm loc}/Z_{\rm loc}$ whenever $Z_{\rm loc}$ is the local factor
associated to $B$ (so that the local term is annihilated under the split $E'/E=F'/F+Z'_{\rm loc}/Z_{\rm loc}$).
Then there is no universal inequality of the form
\[
D_B(W)\ \le\ C\,\delta^{p}\,\Phi_B(E)
\]
(valid for all forcing-aligned boxes under the boundary-contact convention), for any fixed $p>0$ and constant $C$,
unless one supplies a new forcing link that lower-bounds $\Phi_B$ directly under an off-axis quartet.
\end{lemma}

\begin{proof}
This is a structural counterexample: in the class of holomorphic functions $E$ obeying the boundary-contact convention,
take $E=Z_{\rm loc}$ on a box for which $Z_{\rm loc}$ has a zero at one of the dial points $v_\pm$.
Then $F\equiv 1$ and $E'/E=Z'_{\rm loc}/Z_{\rm loc}$, so by assumption $(I-\Pi_B)(E'/E)=0$ and hence $\Phi_B(E)=0$.
However $G_{\rm out}$ is zero-free, so $W=E/G_{\rm out}$ shares the same interior zeros as $E$ and
$W(v_\pm)=0$ for at least one sign, giving $D_B(W)\ge 1$.
Thus no inequality $D_B(W)\le C\delta^{p}\Phi_B(E)$ can hold from these hypotheses alone; any attempt to use such an endpoint
must replace $D_B(W)$ as the forced object and provide a forcing-transfer lemma (Remark~\ref{rem:s5-forceability-gate}).
\end{proof}


\begin{remark}[Consequence for S5 searches]
\label{rem:S5-nogo-consequence}
Lemmas~\ref{prop:S5_Lp_nogo} and \ref{lem:S5-projection-nogo} close two broad endpoint classes:
(i) absolute $L^r(\partial B)$ norms of $E'/E$ (including $L^2$) under the current collar interface,
and (ii) endpoints that annihilate the local kernel span while still targeting the forced dial deviation $D_B(W)$.
Any viable S5 redesign must introduce a genuinely new local-interface input and/or a new forcing-compatible endpoint.
\end{remark}


\medskip
\noindent\textbf{S5 design targets (open).}
A future closure route (S5) should provide a non--pointwise endpoint $\Phi_B$ and a UE--type inequality of the schematic form
\[
D_B(W)\ \le\ C_{\rm up}\,\delta^{p}\,\Phi_B(E)
\qquad (p>0),
\]
together with a local/residual split of $\Phi_B(E)$ whose local contribution scales as $\delta^{-\theta}$ with $\theta<p-\tfrac12$,
or more generally satisfies the exponent budget of Theorem~\ref{thm:exponent-budget}.
The point is \emph{not} to recover the specific exponent $\tfrac32$ from older drafts, but to obtain any effective gain $p-\theta>\tfrac12$
with proof--grade uniformity.

\begin{remark}[Recorded open lemmas (S5 checklist)]
A proof--grade S5 implementation would minimally require:
\begin{enumerate}[leftmargin=1.5em]
\item \textbf{(S5--UE)} a redesigned upper-envelope inequality with a forceable endpoint $\Phi_B$;
\item \textbf{(S5--RES)} a $\delta$--uniform residual envelope bound in the same endpoint class;
\item \textbf{(S5--LOC)} a collar/local bound in the same endpoint class that avoids the pointwise $\delta^{-1}$ blow--up;
\item \textbf{(S5--FORCE)} either $\Phi_B\ge D_B(W)$ or a new forcing lemma as in Remark~\ref{rem:forceability}.
\end{enumerate}
\end{remark}


\section{Global RH from a finite front-end + the tail criterion family}
\label{sec:global}

\begin{theorem}[Global closure (criterion-first logical form)]
\label{thm:global}
Assume:
\begin{enumerate}[leftmargin=1.5em]
\item (Front-end) All nontrivial zeros with $0<\ImPart(s)\le 5$ lie on the critical line.
\item (Tail criterion) Fix some $\eta\in(0,1)$ and $\kappa\in(0,1/10)$, and assume the analytic inputs
Lemmas~\ref{lem:upper-envelope}--\ref{lem:Nloc-logm} and Lemma~\ref{lem:horizontal-budget} with finite constants.
Assume moreover that for every $m\ge 10$ and every $\alpha\in(0,1]$ there exists a $\kappa$--admissible
scale $0<\delta\le \delta_0(m,\alpha)=\eta\alpha/(\log m)^2$ such that the strict tail inequality \eqref{eq:tail-ineq} holds.
\end{enumerate}
Then all nontrivial zeros of $\zeta(s)$ lie on the critical line.
\end{theorem}

\begin{proof}
For each $m\ge 10$, Theorem~\ref{thm:tail-inequality} turns the strict inequality \eqref{eq:tail-ineq}
into exclusion of off-axis quartets at height $m$.
By the tail criterion hypothesis, no off-axis quartets exist at any height $m\ge 10$.
By the front-end hypothesis, there are no off-axis zeros below height $5$.
Hence there are no off-axis zeros at any height, so every nontrivial zero lies on the critical line.
\end{proof}

\begin{remark}[Role of computations and the repro pack (v40)]
Appendix~\ref{app:certificate} provides a small interval-arithmetic harness that evaluates the tail inequality
for pinned parameters and a pinned constant ledger. In v36 this is used only for audit purposes (e.g.\ exponent tracking),
not as a proof substitute.
\end{remark}

\appendix

\section{Discarded closure routes (as of v43)}
\label{app:discarded}

This appendix records closure routes that were explored in earlier iterations (v32--v34) but are now ruled out \emph{under the currently proved inputs}.
The purpose is to prevent future drift: these routes should not be re-opened unless a genuinely new analytic input (e.g.\ an S5 endpoint redesign) is supplied.


\subsection*{D0: Centered defect endpoint closure (S5$^{\rm def}$) is retired}
The v39 ``defect endpoint'' family \(\Phi^{\rm def}\) on centered boxes cannot serve as a load-bearing closure route:
transfer from aligned-box forcing to a centered defect box at the same \(\delta\) is impossible
(Lemma~\ref{lem:ML1-samebox-nogo}); the defect endpoint has a side-length ceiling preventing any \(p>1\) gain from pointwise bounds
(Lemma~\ref{lem:defect-p-ceiling}); and near-resonant quartets can make \(\Phi^{\rm def}\) \(\delta\)-inert
(Lemma~\ref{lem:defect-resonance-nogo}).  The defect endpoint is therefore retained only as a cautionary NO--GO example.


\subsection{D1: Pointwise UE endpoint $\,\sup_{\partial B}|E'/E|$ + collar + $\eta$--absorption (S1/S1$'$)}
The former absorption narrative attempted to close the tail family by shrinking $\eta$ in the nominal scale
$\delta_0(m,\alpha)=\eta\alpha/(\log m)^2$.
In the pointwise/sup architecture the UE step has exponent $p=1$ (Lemma~\ref{lem:upper-envelope}) and the collar/local split has exponent $\theta=1$ (Lemma~\ref{lem:Zloc-logder-collar}),
so the local contribution is $\delta$--inert and cannot be suppressed by $\eta$ (Lemma~\ref{lem:UE-d1-obstruction}).
More strongly, the exponent budget (Theorem~\ref{thm:exponent-budget}) shows that uniform $\eta$--shrinking requires $p-\theta\ge \tfrac12$,
while the scaling NO--GO (Lemma~\ref{lem:UE-scaling-nogo}) forbids any $p>1$ within this endpoint class.
Finally, the forcing margin is constant--limited in the single--box architecture (Lemma~\ref{lem:force-constant-limited}), so one cannot compensate by ``making forcing grow with $m$''.

\begin{proposition}[Historical record: formal anchor absorption under a hypothetical strengthened UE exponent]
\label{prop:eta-absorption-conditional-appx}
This proposition is \emph{not used} in v36. It is recorded only to document the logical shape of the discarded absorption idea.

Assume that, for some $p>1$, an upper-envelope step admits the strengthened form
\[
D_B(W)\ \le\ 2C_{\rm up}\,\delta^{p}\,\sup_{\partial B}\Bigl|\frac{E'}{E}\Bigr|
\]
with the same constant ledger, and that all other constants in \eqref{eq:tail-ineq} are finite.
Fix an anchor height $m_\star\ge 10$ and evaluate \eqref{eq:tail-ineq} at $(m,\alpha)=(m_\star,1)$ with the nominal scale
$\delta_0(m_\star,1)=\eta/(\log m_\star)^2$.
Then there exists $\eta_\star(m_\star,p)>0$ such that \eqref{eq:tail-ineq} holds at $(m_\star,1)$ for every $\eta\in(0,\eta_\star]$.

\smallskip
\noindent\emph{Warning:} within the pointwise/sup endpoint class, Lemma~\ref{lem:UE-scaling-nogo} forbids any $p>1$, so this proposition cannot be invoked without an S5 redesign.
\end{proposition}

\begin{proof}
Under a strengthened exponent $p>1$, the envelope side becomes
$A\,\eta^{p}+B\,\eta^{p-1}$ for finite constants $A,B$ depending on $(m_\star,p)$ and the constant ledger,
while the forcing side equals $c-D\,\eta$ for a finite $D$.
Since $p>1$, one has $\eta^{p}\to 0$, $\eta^{p-1}\to 0$, and $\eta\to 0$ as $\eta\downarrow 0$,
so the strict inequality holds for all sufficiently small $\eta$.
\end{proof}

\subsection{D2: Shrinking the local window / short-interval zero counts}
A tempting workaround is to replace the fixed local window $|\gamma-t|\le 1$ in the residual/collar interface by a shrinking window
$|\gamma-t|\le \delta^\beta$ to reduce the local term.
However, without additional analytic input, available RH--free methods control $N(t+1)-N(t-1)$ at unit scale and do \emph{not} provide a proof--grade bound for
$N(t+\delta^\beta)-N(t-\delta^\beta)$ as $\delta\downarrow 0$.
Thus v36 does not pursue window-shrinking as a substitute for the missing UE gain.

\subsection{D3: ``Make forcing grow with $m$'' within single-box forcing}
Because $\Delta_{I_+}\arg Z_{\rm pair}\le 2\pi$ uniformly (Lemma~\ref{lem:force-constant-limited}), the forcing constant $c$ in the tail inequality is $O(1)$.
Any attempt to obtain a forcing side that grows like $\log m$ (or any unbounded function of $m$) would require a different forcing architecture (not the v36 single-box forcing chain).

\subsection{D4: ``Boundary modulus implies interior zero-freeness'' converse}
Under boundary-contact, the quotient $W=E/G_{\rm out}$ satisfies $|W|=1$ on $\partial B$ (Remark~\ref{rem:boundary_modulus}),
but this has no converse implication toward zero-freeness or constancy (Remark~\ref{rem:no-converse}).
Therefore, any closure route that implicitly treats $|W|=1$ as ``almost zero-free'' is invalid.





\subsection{D5: Absolute $L^r$ log-derivative endpoints (NO--GO)}
Replacing the pointwise endpoint $\sup_{\partial B}|E'/E|$ by an \emph{absolute} boundary $L^r(\partial B)$ norm of $E'/E$
does not improve the exponent budget: Lemma~\ref{lem:S5_Lp_collapse} forces the UE prefactor exponent to be
$p(r)=1-1/r$, while Proposition~\ref{prop:S5_Lp_nogo} shows the local/collar contribution has the same exponent
$\theta(r)=1-1/r$, hence $p(r)-\theta(r)=0$ and the local leakage is $\delta$--inert.

\subsection{D6: Projecting out the local kernel span (NO--GO)}
A tempting idea is to define an endpoint by projecting $E'/E$ off the span of local Cauchy kernels so that the local term vanishes.
Lemma~\ref{lem:S5-projection-nogo} shows this cannot control the forced dial deviation $D_B(W)$ without changing the contradiction endpoint
or supplying a new forcing link.

\medskip
\noindent\emph{Supporting documentation for D6 (not a viable endpoint under current forcing).}
The next definition and lemmas formalize the projection setup and the exact cancellation of the local term.
They are recorded only to document the mechanism behind the NO--GO.



\begin{definition}[Local Cauchy subspace and $L^2$ projection (supporting documentation)]
\label{def:KB-projection}
Let $B=B(\alpha,m,\delta)$ be $\kappa$--admissible and let $Z_{\rm loc}(m)$ denote the multiset
of zeros of $E$ used to define $Z_{\rm loc}$ (counted with multiplicity).
Define the finite-dimensional subspace
\[
K_B:=\mathrm{span}\{\,k_\rho:\partial B\to\mathbb{C},\ k_\rho(v)=(v-\rho)^{-1}\ :\ \rho\in Z_{\rm loc}(m)\,\}
\subset L^2(\partial B,ds),
\]
and let $\Pi_B:L^2(\partial B)\to K_B$ be the orthogonal projection.
\end{definition}


\begin{lemma}[Projection kills the local log-derivative (supporting documentation)]
\label{lem:proj-kills-Zloc}
With notation as in Definition~\ref{def:KB-projection},
\[
\frac{Z'_{\rm loc}}{Z_{\rm loc}}(v)=\sum_{\rho\in Z_{\rm loc}(m)}\frac{m_\rho}{v-\rho}\in K_B
\quad (v\in\partial B).
\]
Hence $\Pi_B(Z'_{\rm loc}/Z_{\rm loc})=Z'_{\rm loc}/Z_{\rm loc}$ and
$(I-\Pi_B)(Z'_{\rm loc}/Z_{\rm loc})=0$ in $L^2(\partial B)$ (and thus pointwise on $\partial B$).
Consequently, using Lemma~\ref{lem:logder-split},
\[
(I-\Pi_B)\!\left(\frac{E'}{E}\right)=(I-\Pi_B)\!\left(\frac{F'}{F}\right)
\quad\text{on }\partial B.
\]
Moreover $\|\Pi_B\|_{L^2\to L^2}=1$.
\end{lemma}


\begin{remark}[Conditioning caveat for coefficient representations (supporting documentation)]
\label{rem:proj-conditioning}
Lemma~\ref{lem:proj-kills-Zloc} uses only the abstract orthogonal projection $\Pi_B$ (a contraction).
No uniform bound on the inverse Gram matrix of the spanning kernels $k_\rho$ is available without
a lower bound on pairwise zero separations in $Z_{\rm loc}(m)$.
Therefore any coefficient-level formula for $\Pi_B$ must be treated as non-uniform unless additional
spacing structure is proved.
\end{remark}



\section{S6 harness: explicit-formula interpretation (non-closure)}
\label{app:S6-harness}

This appendix is an \emph{interpretation harness only}.  It is not used in any implication in the manuscript.
Its purpose is to connect the v--frame ``off-axis'' language to the classical explicit formula for prime-counting functions.



\subsection{D7: ML-$\Delta a$ on aligned boxes is ruled out (v43)}
Lemma~\ref{lem:deltaa-alignedbox-nogo} shows that the two--sided shift--difference endpoint
\(\Phi^{(2\mathrm{s})}_B(a;h)\) cannot be made forceable on the aligned witness family \(B(a,m,\delta)\)
at the nominal micro--step coupling \(h\asymp \delta\asymp \eta a/(\log m)^2\): in the toy quartet model one has
\(\Phi^{(2\mathrm{s})}_B(a;h)\ll \delta h/a^2\to 0\) as \(m\to\infty\).
Therefore, any v40--style ``force \(\Phi^{(2\mathrm{s})}\) on aligned boxes'' closure route is invalid.
Future work must pivot to the v43 GEO--C4 closure lever in Box~\ref{box:geo-c4-v43}:
invent a different witness family and/or a different endpoint coupling that is simultaneously forceable, budget eligible,
and robust under near--resonance.
\subsection{Frame mapping: v--displacement and the real part $\beta$}
A nontrivial zero $\rho=\beta+i\gamma$ in the s--frame corresponds to
\[
u_\rho=2\rho=2\beta+i\,2\gamma,
\qquad
v_\rho=u_\rho-1=(2\beta-1)+i\,2\gamma.
\]
Thus an off-critical-line zero ($\beta\neq \tfrac12$) is exactly an off-axis v--zero ($\Re v_\rho\neq 0$),
with displacement $a:=\Re v_\rho=2\beta-1$.

\subsection{Explicit formula: off-axis zeros as amplitude leaks}
In a standard explicit formula (e.g.\ for $\psi(x)=\sum_{n\le x}\Lambda(n)$), nontrivial zeros enter through terms of the form
$x^\rho/\rho$ (or $\operatorname{Li}(x^\rho)$).  If $\rho=\beta+i\gamma$, then
\[
x^\rho = x^\beta e^{i\gamma\log x},
\]
so the amplitude is governed by $x^\beta$.  In v--variables, $\beta=\tfrac12+\tfrac{a}{2}$, so any $a>0$
corresponds to an $x^{1/2+a/2}$-scale contribution (an ``amplitude leak'' beyond the square-root scale).

\subsection{What S5$'$ would mean in this language}
A successful S5$'$ closure would exclude all off-axis v--zeros, hence prove RH and thereby eliminate all amplitude leaks with $\beta>1/2$.
However, the present manuscript does \emph{not} claim any new prime-error bounds directly: the S6 harness is only a translation layer
for interpreting off-axis zeros in the classical explicit-formula setting.


\paragraph{S6 cross-check for GEO--C4.}
The GEO--C4 endpoint $\Phi^\star$ is a \emph{tilt-sensitivity functional}, but now read through a hinge-centered \emph{harmonic channel}.
It acts on the double-difference field $\mathcal D_{a,h}$, i.e.\ a second finite difference in the shift parameter $a$ of the log-derivative $E'/E$,
sampled on the hinge circle $C_{m,\delta}$ and then orthogonally projected onto the $k=2$ Fourier carrier.

In explicit-formula language, varying $a$ corresponds to varying $\beta=\tfrac12+\tfrac a2$, i.e.\ changing the exponent in the zero-term $x^\rho=x^{\beta+i\gamma}$.
An off-axis quartet at tilt $a>0$ produces an amplitude leak factor $x^{a/2}$ relative to the critical-line baseline.
GEO--C4 is engineered so that such a leak yields a nonzero local dipole kernel for $\mathcal D_{a,h}$ near $v=i m$, which forces a $k=2$ boundary harmonic (Lemma~\ref{lem:geo-c4-toy-force}),
while UE control can be pursued via derivative field bounds rather than a pointwise supremum (Box~\ref{box:ue-input-v43}).


\section{Tail harness bundle and reproducibility (v43)}
\label{app:repro}
\label{app:certificate}

\subsection{What the tail checks prove (and what they do not)}
\label{app:what-proves}

Each tail check records the statement:
\begin{quote}
Given a constants file that provides interval enclosures for
$(C_1,C_2,C_{\mathrm{up}},C_h'',\kappa)$, the chosen parameters $(m,\eta,\alpha)$,
and the recorded UE exponent $p$,
the harness computes interval bounds for the left-hand side $\mathrm{LHS}$ and right-hand side $\mathrm{RHS}$ in
\eqref{eq:tail-ineq} and reports whether the strict separation $\mathrm{LHS}_{\mathrm{hi}}<\mathrm{RHS}_{\mathrm{lo}}$ holds.
\end{quote}


It does \emph{not} certify that the constants file is correct.

\subsection{SHA--256 table (exact artifacts)}
\label{app:sha}

The file \texttt{v40\_repro\_pack/SHA256SUMS.txt} is the canonical hash list.

\lstinputlisting{v43_repro_pack/SHA256SUMS.txt}

\subsection{Commands}
\label{app:commands}

From the directory \texttt{v40\_repro\_pack/}:
\begin{enumerate}[leftmargin=1.5em]
\item \texttt{sha256sum -c SHA256SUMS.txt}
\item \texttt{python3 v36\_verify\_tail\_check.py --constants v36\_constants\_m10.json --certificate v36\_tail\_check\_m10.json}
\item \texttt{python3 v36\_verify\_frontend\_certificate.py --certificate v36\_frontend\_certificate.json}
\end{enumerate}

\subsection{Expected verifier output: $m=10$ (verbatim; may report strict inequality as false)}
\label{app:verifier-output-10}
\lstinputlisting{v43_repro_pack/v41_tail_check_verifier_output_m10.txt}

\subsection{Bundle files (verbatim)}
\label{app:bundle-files}

\paragraph{v36 low-anchor constants (intervals; audit harness).}
\lstinputlisting{v43_repro_pack/v41_constants_m10.json}

\paragraph{v36 low-anchor tail check ($m=10$).}
\lstinputlisting{v43_repro_pack/v41_tail_check_m10.json}

\paragraph{Generator implementation (directed rounding).}
\lstinputlisting{v43_repro_pack/v41_generate_tail_check.py}

\paragraph{Verifier implementation.}
\lstinputlisting{v43_repro_pack/v41_verify_tail_check.py}

\section{Finite-height front-end certificate (literature-based)}
\label{app:frontend}

The required front-end is RH up to height $H_0=5$.
We record a discharge using Platt--Trudgian's published verification of RH up to
$3\cdot 10^{12}$.

\paragraph{Pinned front-end certificate JSON.}
\lstinputlisting{v43_repro_pack/v41_frontend_certificate.json}

\paragraph{Front-end verifier output (internal logic only).}
\lstinputlisting{v43_repro_pack/v41_frontend_verifier_output.txt}

\paragraph{Generator/verifier scripts.}
\lstinputlisting{v43_repro_pack/v41_generate_frontend_certificate.py}
\lstinputlisting{v43_repro_pack/v41_verify_frontend_certificate.py}
\section*{References}
\addcontentsline{toc}{section}{References}

\begin{thebibliography}{99}

\bibitem{CMM82}
R.~Coifman, A.~McIntosh, and Y.~Meyer,
\emph{L'int\'egrale de Cauchy d\'efinit un op\'erateur born\'e sur $L^2$ pour les courbes lipschitziennes},
Annals of Mathematics (2) \textbf{116} (1982), no.~2, 361--387.

\bibitem{DriscollTrefethenSC}
T.~A. Driscoll and L.~N. Trefethen,
\emph{Schwarz--Christoffel Mapping},
Cambridge Monographs on Applied and Computational Mathematics, Cambridge University Press, 2002.

\bibitem{DurenHp}
P.~L. Duren,
\emph{Theory of $H^p$ Spaces},
Academic Press, 1970.

\bibitem{GarnettBaf}
J.~B. Garnett,
\emph{Bounded Analytic Functions},
Graduate Texts in Mathematics, Springer, 2007.

\bibitem{Ivic}
A.~Ivi\'c,
\emph{The Riemann Zeta-Function: Theory and Applications},
Wiley-Interscience, 1985.

\bibitem{Titchmarsh}
E.~C. Titchmarsh,
\emph{The Theory of the Riemann Zeta-Function}, 2nd ed., revised by D.~R. Heath-Brown,
Oxford University Press, 1986.

\bibitem{BellottiWongZeta2024}
A.~Bellotti and T.~Wong,
\emph{An improved explicit bound on the argument of the Riemann zeta function on the critical line},
arXiv:2412.15470v2 (2024).

\bibitem{PlattTrudgian2021}
D.~Platt and T.~Trudgian,
\emph{The Riemann hypothesis is true up to $3\cdot 10^{12}$},
Bulletin of the London Mathematical Society \textbf{53} (2021), no.~3, 792--797.
\end{thebibliography}


\end{document}
